---
title: "Cluster analysis of the PBMC aggregated (4 time periods)"
author: "Kushal K Dey"
date: "8/4/2017"
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(CountClust)
library(maptpx)
library(ggplot2)
library(MAST)
library(GSEABase)
library(Seurat)
```

```{r echo=TRUE, eval=TRUE}
counts1 <- get(load("../output/GS_PBMC_10_2016_GRN0760.rda"))
counts2<- get(load("../output/GS_PBMC_2_2015_GRN0304.rda"))
counts3<- get(load("../output/GS_PBMC_2_2016_GRN0535.rda"))
counts4<- get(load("../output/GS_PBMC_8_2013_MCCB1050.rda"))

counts1 <- as.matrix(counts1)
counts2<- as.matrix(counts2)
counts3<- as.matrix(counts3)
counts4<- as.matrix(counts4)

aggregated_data <- rbind(counts1, counts2, counts3, counts4)
rownames(aggregated_data) <- 1:dim(aggregated_data)[1]
dim(aggregated_data)
```

```{r echo=TRUE, eval=TRUE}
fac <- c(rep("Oct-2016", dim(counts1)[1]),rep("Feb-2015", dim(counts2)[1]),
             rep("Feb-2016", dim(counts3)[1]), rep("Aug-2013", dim(counts4)[1]))
fac <- factor(fac, levels = c("Aug-2013", "Feb-2015", "Feb-2016", "Oct-2016"))
length(fac)
```

```{r echo=FALSE, eval=FALSE}
rownames(aggregated_data) <- 1:dim(aggregated_data)[1]
seuratObj <- new('seurat', raw.data = t(aggregated_data))
seuratObj <- Setup(seuratObj, min.cells = 0, min.genes = 0, project = 'Pantaleo', total.expr = 10000) # no need to filter - already done
#- Output
seuratObj_TFH_global <- seuratObj
```

```{r echo=FALSE, eval=FALSE}
seuratObj_TFH_global <- MeanVarPlot(seuratObj_TFH_global, fxn.x = expMean, fxn.y = logVarDivMean, x.low.cutoff = 0.25, x.high.cutoff = 3, y.cutoff = 0.5, do.contour = FALSE)
length(seuratObj_TFH_global@var.genes)
seuratObj_TFH_global <- PCA(seuratObj_TFH_global, pc.genes = seuratObj_TFH_global@var.genes)
seuratObj_TFH_global <- ProjectPCA(seuratObj_TFH_global)
VizPCA(seuratObj_TFH_global, 1:2)
```

```{r echo=FALSE, eval= FALSE}
save(seuratObj_TFH_global, file = "../output/seurat_aggregated_mcc_2.rda")
```

```{r echo=FALSE, eval=TRUE}
seuratObj_TFH_global <- get(load("../output/seurat_aggregated_after_tsne.Robj"))
#tsne_data <- get(load("../output/tsne_seurat_aggregated_mcc.rda"))
#seuratObj_TFH_global@tsne.rot <- data.frame(tsne_data)
```

## t-SNE projection

```{r echo=FALSE, eval=TRUE}
labels <- fac
#nUMI <- seuratObj_TFH_global@data.info$nUMI
#nGene <- seuratObj_TFH_global@data.info$nGene

data_ggplot <- data.frame(labels = labels,
                          tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2])

```


```{r echo=FALSE, eval=TRUE}
plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```

## Cluster analysis

```{r echo=FALSE, eval=TRUE}
topic_clus <- get(load("../output/maptpx_aggregated_MCC.rda"))
```

```{r echo=FALSE, eval=TRUE}
PlotCountClust <- function(topic_clus, fac){
  omega <- topic_clus$omega
  theta <- topic_clus$theta
  
  annotation <- data.frame(
    sample_id = paste0("X", 1:length(fac)),
    tissue_label = factor(fac,
                          levels = rev(unique(fac) ) ) );

  rownames(omega) <- annotation$sample_id;
  
  StructureGGplot(omega = omega,
                  annotation = annotation,
                  palette = RColorBrewer::brewer.pal(8, "Accent"),
                  yaxis_label = "Types",
                  order_sample = TRUE,
                  axis_tick = list(axis_ticks_length = .1,
                                   axis_ticks_lwd_y = .1,
                                   axis_ticks_lwd_x = .1,
                                   axis_label_size = 7,
                                   axis_label_face = "bold"))
}

```

```{r}
PlotCountClust(topic_clus[[2]], fac)
PlotCountClust(topic_clus[[3]], fac)
PlotCountClust(topic_clus[[4]], fac)
PlotCountClust(topic_clus[[5]], fac)
PlotCountClust(topic_clus[[6]], fac)
PlotCountClust(topic_clus[[7]], fac)
PlotCountClust(topic_clus[[8]], fac)
```

## t-SNE projection + CountClust coloring

```{r fig.height = 6, echo=FALSE, eval=TRUE}
labels2 <- as.factor(apply(topic_clus[[2]]$omega, 1, function(x) return(which.max(x))))
labels3 <- as.factor(apply(topic_clus[[3]]$omega, 1, function(x) return(which.max(x))))
labels4 <- as.factor(apply(topic_clus[[4]]$omega, 1, function(x) return(which.max(x))))
labels5 <- as.factor(apply(topic_clus[[5]]$omega, 1, function(x) return(which.max(x))))
labels6 <- as.factor(apply(topic_clus[[6]]$omega, 1, function(x) return(which.max(x))))

data_ggplot <- data.frame(labels2 = labels2,
                          labels3 = labels3,
                          labels4 = labels4,
                          labels5 = labels5,
                          labels6 = labels6,
                          tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels2), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels3), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels4), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels5), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels6), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')

plot_grid(plot1, plot2, plot3, plot4, plot5, ncol = 2, align = 'v')
```

## K=2 driving genes

### cluster 1

```{r echo=FALSE, eval=TRUE}
indices <- ExtractTopFeatures(topic_clus[[2]]$theta, top_features = 100, method = "poisson", options = "max")
imp_genes <- apply(indices$indices, 1, function(x) return(colnames(counts6)[x]))

out <- mygene::queryMany(imp_genes[1:20,1],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
tab <- cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
colnames(tab) <- c("symbol", "name")
rownames(tab) <- NULL
tab
```

### cluster 2

```{r echo=FALSE, eval=TRUE}
out <- mygene::queryMany(imp_genes[1:50,2],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
tab <- cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
colnames(tab) <- c("symbol", "name")
rownames(tab) <- NULL
tab
```


## K=2 t-SNE gene expression

### cluster 1 imp genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- imp_genes[1:6,1]

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6,  ncol = 2, align = 'v')
```

### cluster 2 imp genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- imp_genes[1:6,2]

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6,  ncol = 2, align = 'v')
```


## K=3 driving genes

### cluster 1

```{r echo=FALSE, eval=TRUE}
indices <- ExtractTopFeatures(topic_clus[[3]]$theta, top_features = 100, method = "poisson", options = "max")
imp_genes <- apply(indices, 1, function(x) return(colnames(counts6)[x]))

out <- mygene::queryMany(imp_genes[1:20,1],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
tab <- cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
colnames(tab) <- c("symbol", "name")
rownames(tab) <- NULL
tab
```

### cluster 2

```{r echo=FALSE, eval=TRUE}
out <- mygene::queryMany(imp_genes[1:20,2],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
tab <- cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
colnames(tab) <- c("symbol", "name")
rownames(tab) <- NULL
tab
```

### cluster 3

```{r echo=FALSE, eval=TRUE}
out <- mygene::queryMany(imp_genes[1:20,3],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
tab <- cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
colnames(tab) <- c("symbol", "name")
rownames(tab) <- NULL
tab
```

## K=3 t-SNE gene expression

### cluster 1 imp genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- imp_genes[1:6,1]

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6,  ncol = 2, align = 'v')
```

### cluster 2 imp genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- imp_genes[1:6,2]

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6,  ncol = 2, align = 'v')
```


### cluster 3 imp genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- imp_genes[1:6,3]

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6,  ncol = 2, align = 'v')
```

## K=6 driving genes

### cluster 1

```{r echo=FALSE, eval=TRUE}
indices <- ExtractTopFeatures(topic_clus[[6]]$theta, top_features = 100, method = "poisson", options = "max")
imp_genes <- apply(indices, 1, function(x) return(colnames(counts6)[x]))

out <- mygene::queryMany(imp_genes[1:20,1],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
tab <- cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
colnames(tab) <- c("symbol", "name")
rownames(tab) <- NULL
tab
```

### cluster 2

```{r echo=FALSE, eval=TRUE}
out <- mygene::queryMany(imp_genes[1:20,2],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
tab <- cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
colnames(tab) <- c("symbol", "name")
rownames(tab) <- NULL
tab
```

### cluster 3

```{r echo=FALSE, eval=TRUE}
out <- mygene::queryMany(imp_genes[1:20,3],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
tab <- cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
colnames(tab) <- c("symbol", "name")
rownames(tab) <- NULL
tab
```


### cluster 4

```{r echo=FALSE, eval=TRUE}
out <- mygene::queryMany(imp_genes[1:20,4],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
tab <- cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
colnames(tab) <- c("symbol", "name")
rownames(tab) <- NULL
tab
```


### cluster 5

```{r echo=FALSE, eval=TRUE}
out <- mygene::queryMany(imp_genes[1:20,5],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
tab <- cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
colnames(tab) <- c("symbol", "name")
rownames(tab) <- NULL
tab
```


### cluster 6

```{r echo=FALSE, eval=TRUE}
out <- mygene::queryMany(imp_genes[1:20,6],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
tab <- cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
colnames(tab) <- c("symbol", "name")
rownames(tab) <- NULL
tab
```


## K=6 t-SNE gene expression

### cluster 1 imp genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- imp_genes[1:6,1]

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6,  ncol = 2, align = 'v')
```

### cluster 2 imp genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- imp_genes[1:6,2]

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6,  ncol = 2, align = 'v')
```


### cluster 3 imp genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- imp_genes[1:6,3]

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6,  ncol = 2, align = 'v')
```


### cluster 4 imp genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- imp_genes[1:6,4]

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6,  ncol = 2, align = 'v')
```

### cluster 5 imp genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- imp_genes[1:6,5]

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6,  ncol = 2, align = 'v')
```

### cluster 6 imp genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- imp_genes[1:6,6]

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6,  ncol = 2, align = 'v')
```


## t-SNE projection of common marker genes

We take some markers for T-cells, B cells and NK cells next, and see which cluster they correspond to ?
We use markers CD3D (T cell receptor complex), CD79A (B cells), CD4 (B cells), CLEC4C (B cells), NKG7 (Natural killer cells), FCER1A (dendritic), CD16, S100A8 (myeloid cells) and S100A9 (myeloid cells), CCR10 (memory T cells), TNFRSF18 (memory T cells), PF4 (megakaryocytes), SIGLEC7 (NK cells), GZMK, CD8A (CD8+ T cells) as per Zheng et al paper. 

```{r fig.height = 12, echo=FALSE, eval=TRUE}
cex.size = 2
genes <- c("CD3D", "GZMK", "CD8A", "CD79A", "CD4", "CLEC4C", "S100A8", "S100A9", "CCR10",
           "TNFRSF18", "PF4", "NKG7", "SIGLEC7", "FCER1A")
match(genes, colnames(counts6))

data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ],
                          Third = seuratObj_TFH_global@data[paste0(genes[3]), ], # LiveCells marker
                          Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ],
                          Seventh = seuratObj_TFH_global@data[paste0(genes[7]), ],
                          Eigth = seuratObj_TFH_global@data[paste0(genes[8]), ],
                          Ninth = seuratObj_TFH_global@data[paste0(genes[9]), ],
                          Tenth = seuratObj_TFH_global@data[paste0(genes[10]), ],
                          Eleventh = seuratObj_TFH_global@data[paste0(genes[11]), ],
                          Twelfth = seuratObj_TFH_global@data[paste0(genes[12]), ],
                          Thirteenth = seuratObj_TFH_global@data[paste0(genes[13]), ],
                          Fourteenth = seuratObj_TFH_global@data[paste0(genes[14]), ]
 ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes[3]))

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes[5]))

plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes[6]))

plot7 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Seventh), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[7]), ], 0.2),  name = paste0(genes[7]))

plot8 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Eigth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[8]), ], 0.2),  name = paste0(genes[8]))

plot9 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Ninth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[9]), ], 0.2),  name = paste0(genes[9]))

plot10 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Tenth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[10]), ], 0.2),  name = paste0(genes[10]))

plot11 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Eleventh), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[11]), ], 0.2),  name = paste0(genes[11]))

plot12 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Twelfth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[12]), ], 0.2),  name = paste0(genes[12]))

plot13 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Thirteenth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[13]), ], 0.2),  name = paste0(genes[13]))

plot14 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourteenth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[14]), ], 0.2),  name = paste0(genes[14]))

plot_grid(plot1, plot2, plot3, plot4, plot5, plot6, 
          plot7, plot8, plot9, plot10, plot11, plot12, plot13, plot14,
          ncol = 2, align = 'v')
```




## GSEA 

We perform gene set enrichment analysis on the theta matrices, reprsenting the three clusters, obtained from fitting CountClust on the Live + LN cells.

```{r echo=FALSE, eval=TRUE}
theta <- topic_clus[[3]]$theta
theta2 <- t(apply(theta, 1, function(x) return((x - mean(x))/sd(x))))
```

We extract gene names in pathways from the MAST package 

```{r echo=FALSE, eval=TRUE}
module <- "BTM"
min_gene_in_module <- 5
packageExt <- system.file("extdata", package='MAST')
module_file <- list.files(packageExt, pattern = module, full.names = TRUE)
gene_set <- getGmt(module_file)
gene_ids <- geneIds(gene_set)
```

### First cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,1])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),1:2]
```

### Second cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,2])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),1:2]
```

### Third cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,3])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),1:2]
```

