---
title: "SVM vs classtpx training for Jurkat + 293T data (50-50) data"
author: "Kushal K Dey"
date: "9/24/2017"
output: html_document
---

## Data Processing

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(CountClust)
library(maptpx)
library(ggplot2)
library(GSEABase)
library(Seurat)
library(classtpx)
library(e1071)
library(plyr)
```


```{r echo=FALSE, eval=TRUE}
seuratObj_TFH_global <- get(load("../output/seurat_jurkat_293T_50_50.rda"))
fac <- rep("jurkat_293T", dim(seuratObj_TFH_global@data)[2])
```

```{r}
jurkat_data <- Read10X("../data/jurkat/filtered_matrices_mex/hg19/")
dim(jurkat_data)
```

```{r}
t_data <- Read10X("../data/293T/filtered_matrices_mex/hg19/")
dim(t_data)
```

```{r}
data3 <- seuratObj_TFH_global@raw.data
```


```{r}
intersected_genes <- intersect(rownames(data3), intersect(rownames(jurkat_data), rownames(t_data)))
```

```{r}
data3_filt <- data3[match(intersected_genes, rownames(data3)), ]
jurkat_data_filt <- jurkat_data[match(intersected_genes, rownames(jurkat_data)),]
t_data_filt <- t_data[match(intersected_genes, rownames(t_data)),]
```

```{r}
pooled_jurkat_t_data <- rbind(t(jurkat_data_filt), t(t_data_filt))
class_labs <- c(rep("jurkat", dim(jurkat_data_filt)[2]), rep("293T", dim(t_data_filt)[2]))
```

## Subsampling rate : 0.25

Subsampling from this data to form training and test samples.

```{r}
train_subsamples <- sample(1:length(class_labs), 1500, replace = FALSE)
table(class_labs[train_subsamples])
```

### svm application

```{r}
svm_data <- pooled_jurkat_t_data[, match(seuratObj_TFH_global@var.genes, colnames(pooled_jurkat_t_data))]
```

```{r}
train_data <- as.matrix(svm_data[train_subsamples,])
test_data <- as.matrix(svm_data[-train_subsamples,])
dim(train_data)
dim(test_data)
class_labs_train <- class_labs[train_subsamples]
class_labs_test <- class_labs[-train_subsamples]
dat <- cbind.data.frame(train_data, class_labs_train)
```

```{r}
svm.control.default <- list(scale = TRUE, type = NULL, kernel ="radial",
                              degree = 3,
                              coef0 = 0, cost = 1, nu = 0.5,
                              class.weights = NULL, cachesize = 40, tolerance = 0.001, 
                              epsilon = 0.1,
                              shrinking = TRUE, cross = 0, fitted = TRUE)
svm.control <- list()
svm.control <- modifyList(svm.control.default, svm.control)


model_SVM <- do.call(e1071::svm, append(list(formula = class_labs_train ~ ., data=dat, probability=TRUE), svm.control))
prob  = predict(model_SVM, test_data, probability=TRUE)
length(which(prob != class_labs_test))/length(prob)
```

```{r}
known_samples <- train_subsamples
class_labs_train_2 <- factor(as.vector(plyr::mapvalues(class_labs_train, from = unique(class_labs), to = 1:length(unique(class_labs)))))
```

### classtpx application (subsetted)

```{r echo=FALSE, eval=TRUE}
topic_clus <- classtpx::class_topics(svm_data, K=2, known_samples = known_samples, class_labs = class_labs_train_2, method = "theta.fix", shrink = FALSE, tol = 0.001, ord=FALSE)
```

```{r}
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x) return(which.max(x))))
labels2_class <- unique(class_labs)[labels2]
length(which(labels2_class[-train_subsamples] != class_labs_test))/length(class_labs_test)
```

### classtpx application (full)

```{r echo=FALSE, eval=FALSE}
topic_clus <- classtpx::class_topics(pooled_jurkat_t_data, K=2, known_samples = known_samples, class_labs = class_labs_train_2, method = "theta.fix", shrink = FALSE, tol = 0.001, ord=FALSE)
save(topic_clus, file = "../output/classtpx_jurkat_T293_train_test_1.rda")
```

```{r}
topic_clus <- get(load(file = "../output/classtpx_jurkat_T293_train_test_1.rda"))
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x) return(which.max(x))))
labels2_class <- unique(class_labs)[labels2]
length(which(labels2_class[-train_subsamples] != class_labs_test))/length(class_labs_test)
```



## Subsampling rate : 0.5

Subsampling from this data to form training and test samples.

```{r}
train_subsamples <- sample(1:length(class_labs), 3000, replace = FALSE)
table(class_labs[train_subsamples])
```

### svm application

```{r}
svm_data <- pooled_jurkat_t_data[, match(seuratObj_TFH_global@var.genes, colnames(pooled_jurkat_t_data))]
```

```{r}
train_data <- as.matrix(svm_data[train_subsamples,])
test_data <- as.matrix(svm_data[-train_subsamples,])
dim(train_data)
dim(test_data)
class_labs_train <- class_labs[train_subsamples]
class_labs_test <- class_labs[-train_subsamples]
dat <- cbind.data.frame(train_data, class_labs_train)
```

```{r}
svm.control.default <- list(scale = TRUE, type = NULL, kernel ="radial",
                              degree = 3,
                              coef0 = 0, cost = 1, nu = 0.5,
                              class.weights = NULL, cachesize = 40, tolerance = 0.001, 
                              epsilon = 0.1,
                              shrinking = TRUE, cross = 0, fitted = TRUE)
svm.control <- list()
svm.control <- modifyList(svm.control.default, svm.control)


model_SVM <- do.call(e1071::svm, append(list(formula = class_labs_train ~ ., data=dat, probability=TRUE), svm.control))
prob  = predict(model_SVM, test_data, probability=TRUE)
length(which(prob != class_labs_test))/length(prob)
```

```{r}
known_samples <- train_subsamples
class_labs_train_2 <- factor(as.vector(plyr::mapvalues(class_labs_train, from = unique(class_labs), to = 1:length(unique(class_labs)))))
```

### classtpx application (subsetted)

```{r echo=FALSE, eval=TRUE}
topic_clus <- classtpx::class_topics(svm_data, K=2, known_samples = known_samples, class_labs = class_labs_train_2, method = "theta.fix", shrink = FALSE, tol = 0.001, ord=FALSE)
```

```{r}
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x) return(which.max(x))))
labels2_class <- unique(class_labs)[labels2]
length(which(labels2_class[-train_subsamples] != class_labs_test))/length(class_labs_test)
```

### classtpx application (full)

```{r echo=FALSE, eval=FALSE}
topic_clus <- classtpx::class_topics(pooled_jurkat_t_data, K=2, known_samples = known_samples, class_labs = class_labs_train_2, method = "theta.fix", shrink = FALSE, tol = 0.001, ord=FALSE)
save(topic_clus, file = "../output/classtpx_jurkat_T293_train_test_2.rda")
```

```{r}
topic_clus <- get(load(file = "../output/classtpx_jurkat_T293_train_test_2.rda"))
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x) return(which.max(x))))
labels2_class <- unique(class_labs)[labels2]
length(which(labels2_class[-train_subsamples] != class_labs_test))/length(class_labs_test)
```

## Subsampling rate : 0.75

Subsampling from this data to form training and test samples.

```{r}
train_subsamples <- sample(1:length(class_labs), 4500, replace = FALSE)
table(class_labs[train_subsamples])
```

### svm application

```{r}
svm_data <- pooled_jurkat_t_data[, match(seuratObj_TFH_global@var.genes, colnames(pooled_jurkat_t_data))]
```

```{r}
train_data <- as.matrix(svm_data[train_subsamples,])
test_data <- as.matrix(svm_data[-train_subsamples,])
dim(train_data)
dim(test_data)
class_labs_train <- class_labs[train_subsamples]
class_labs_test <- class_labs[-train_subsamples]
dat <- cbind.data.frame(train_data, class_labs_train)
```

```{r}
svm.control.default <- list(scale = TRUE, type = NULL, kernel ="radial",
                              degree = 3,
                              coef0 = 0, cost = 1, nu = 0.5,
                              class.weights = NULL, cachesize = 40, tolerance = 0.001, 
                              epsilon = 0.1,
                              shrinking = TRUE, cross = 0, fitted = TRUE)
svm.control <- list()
svm.control <- modifyList(svm.control.default, svm.control)


model_SVM <- do.call(e1071::svm, append(list(formula = class_labs_train ~ ., data=dat, probability=TRUE), svm.control))
prob  = predict(model_SVM, test_data, probability=TRUE)
length(which(prob != class_labs_test))/length(prob)
```

```{r}
known_samples <- train_subsamples
class_labs_train_2 <- factor(as.vector(plyr::mapvalues(class_labs_train, from = unique(class_labs), to = 1:length(unique(class_labs)))))
```

### classtpx application (subsetted)

```{r echo=FALSE, eval=TRUE}
topic_clus <- classtpx::class_topics(svm_data, K=2, known_samples = known_samples, class_labs = class_labs_train_2, method = "theta.fix", shrink = FALSE, tol = 0.001, ord=FALSE)
```

```{r}
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x) return(which.max(x))))
labels2_class <- unique(class_labs)[labels2]
length(which(labels2_class[-train_subsamples] != class_labs_test))/length(class_labs_test)
```

### classtpx application (full)

```{r echo=FALSE, eval=FALSE}
topic_clus <- classtpx::class_topics(pooled_jurkat_t_data, K=2, known_samples = known_samples, class_labs = class_labs_train_2, method = "theta.fix", shrink = FALSE, tol = 0.001, ord=FALSE)
save(topic_clus, file = "../output/classtpx_jurkat_T293_train_test_3.rda")
```

```{r}
topic_clus <- get(load(file = "../output/classtpx_jurkat_T293_train_test_3.rda"))
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x) return(which.max(x))))
labels2_class <- unique(class_labs)[labels2]
length(which(labels2_class[-train_subsamples] != class_labs_test))/length(class_labs_test)
```
