---
title: "The coefficient of variation versus mean plots (HIV+ and HIV- patients)"
author: "Kushal K Dey"
date: "8/1/2017"
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(Seurat)
library(plyr)
library(dplyr)
library(Matrix)
library(cowplot)
library(stringr)
library(MAST)
library(doMC)
library(pheatmap)
library(grid)
library(stringr)
library(maptpx)
library(CountClust)
library(ggplot2)
library(GGally)
library(GSEABase)
library(limma)
library(reshape2)
library(data.table)
library(knitr)
library(TxDb.Hsapiens.UCSC.hg19.knownGene)
library(stringr)
library(NMF)
library(rsvd)
library(RColorBrewer)
library(MAST)
```

In this script, we plot the coefficient of variation against the mean expression patterns of the
genes for each study case (HIV+ and HIV-). We know that the points that act as outliers in this
plot do not fit the Poisson model well. We here try to observe if there is a pattern among the 
genes that show large deviations from this model. Are these genes related? Are they part of the same functional group or pathway?

## TFH146

### TFH sorted cells


```{r echo=FALSE, eval=TRUE}
seuratObj_TFH_global <- get(load("../output/TFH146/seuratTFH.rda"))
```

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
###--- Regress out unwanted sources of variation
mito.genes <- grep("^MT-", rownames(seuratObj_TFH_global@data), value = TRUE)
percent.mito <- colSums(as.matrix(expm1(seuratObj_TFH_global@data[mito.genes, ]))) / colSums(as.matrix(expm1(seuratObj_TFH_global@data)))
seuratObj_TFH_global <- AddMetaData(seuratObj_TFH_global, percent.mito, 'percent.mito')
GenePlot(seuratObj_TFH_global, 'nUMI', 'percent.mito')
GenePlot(seuratObj_TFH_global, 'nUMI', 'nGene')
#- remove unwanted sources of variation
seuratObj_TFH_global <- RegressOut(seuratObj_TFH_global, latent.vars = c('nUMI', 'percent.mito')) # remove effect of CDR (high correlation between nGene and nUMI - 0.97) and mitochondrial
```

Mean variance plot
```{r echo=FALSE, eval=TRUE}
seuratObj_TFH_global <- MeanVarPlot(seuratObj_TFH_global, fxn.x = expMean, fxn.y = logVarDivMean, x.low.cutoff = 0.25, x.high.cutoff = 3, y.cutoff = 0.5, do.contour = FALSE)
length(seuratObj_TFH_global@var.genes)
```

Pathway analysis of the normed mean variance measure calculated from Seurat.

```{r echo=FALSE, eval=TRUE}
module <- "BTM"
min_gene_in_module <- 5
packageExt <- system.file("extdata", package='MAST')
module_file <- list.files(packageExt, pattern = module, full.names = TRUE)
gene_set <- getGmt(module_file)
gene_ids <- geneIds(gene_set)
```

```{r echo=FALSE, eval=TRUE}
vec <- seuratObj_TFH_global@mean.var$data.norm.y
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE)[1:20],]
```

### Live Cells

```{r echo=FALSE, eval=TRUE}
seuratObj_LiveCells_global <- get(load("../output/TFH146/seuratLiveCells.rda"))
```

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
###--- Regress out unwanted sources of variation
mito.genes <- grep("^MT-", rownames(seuratObj_LiveCells_global@data), value = TRUE)
percent.mito <- colSums(as.matrix(expm1(seuratObj_LiveCells_global@data[mito.genes, ]))) / colSums(as.matrix(expm1(seuratObj_LiveCells_global@data)))
seuratObj_LiveCells_global <- AddMetaData(seuratObj_LiveCells_global, percent.mito, 'percent.mito')
GenePlot(seuratObj_LiveCells_global, 'nUMI', 'percent.mito')
GenePlot(seuratObj_LiveCells_global, 'nUMI', 'nGene')
#- remove unwanted sources of variation
seuratObj_LiveCells_global <- RegressOut(seuratObj_LiveCells_global, latent.vars = c('nUMI', 'percent.mito')) # remove effect of CDR (high correlation between nGene and nUMI - 0.97) and mitochondrial
```

```{r echo=FALSE, eval=TRUE}
seuratObj_LiveCells_global <- MeanVarPlot(seuratObj_LiveCells_global, fxn.x = expMean, fxn.y = logVarDivMean, x.low.cutoff = 0.25, x.high.cutoff = 3, y.cutoff = 0.5, do.contour = FALSE)
length(seuratObj_LiveCells_global@var.genes)
```

```{r echo=FALSE, eval=TRUE}
module <- "BTM"
min_gene_in_module <- 5
packageExt <- system.file("extdata", package='MAST')
module_file <- list.files(packageExt, pattern = module, full.names = TRUE)
gene_set <- getGmt(module_file)
gene_ids <- geneIds(gene_set)
```

```{r echo=FALSE, eval=TRUE}
vec <- seuratObj_LiveCells_global@mean.var$data.norm.y
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE)[1:20],]
```



## TFH095

### TFH sorted cells


```{r echo=FALSE, eval=TRUE}
seuratObj_TFH_global <- get(load("../output/TFH095/seuratTFH.rda"))
```

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
###--- Regress out unwanted sources of variation
mito.genes <- grep("^MT-", rownames(seuratObj_TFH_global@data), value = TRUE)
percent.mito <- colSums(as.matrix(expm1(seuratObj_TFH_global@data[mito.genes, ]))) / colSums(as.matrix(expm1(seuratObj_TFH_global@data)))
seuratObj_TFH_global <- AddMetaData(seuratObj_TFH_global, percent.mito, 'percent.mito')
GenePlot(seuratObj_TFH_global, 'nUMI', 'percent.mito')
GenePlot(seuratObj_TFH_global, 'nUMI', 'nGene')
#- remove unwanted sources of variation
seuratObj_TFH_global <- RegressOut(seuratObj_TFH_global, latent.vars = c('nUMI', 'percent.mito')) # remove effect of CDR (high correlation between nGene and nUMI - 0.97) and mitochondrial
```


```{r echo=FALSE, eval=TRUE}
seuratObj_TFH_global <- MeanVarPlot(seuratObj_TFH_global, fxn.x = expMean, fxn.y = logVarDivMean, x.low.cutoff = 0.25, x.high.cutoff = 3, y.cutoff = 0.5, do.contour = FALSE)
length(seuratObj_TFH_global@var.genes)
```

Pathway analysis of the normed mean variance measure calculated from Seurat.

```{r echo=FALSE, eval=TRUE}
module <- "BTM"
min_gene_in_module <- 5
packageExt <- system.file("extdata", package='MAST')
module_file <- list.files(packageExt, pattern = module, full.names = TRUE)
gene_set <- getGmt(module_file)
gene_ids <- geneIds(gene_set)
```

```{r echo=FALSE, eval=TRUE}
vec <- sort(seuratObj_TFH_global@mean.var$data.norm.y, decreasing = TRUE)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE)[1:20],]
```

### Live Cells

```{r echo=FALSE, eval=TRUE}
seuratObj_LiveCells_global <- get(load("../output/TFH095/seuratLiveCells.rda"))
```

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
###--- Regress out unwanted sources of variation
mito.genes <- grep("^MT-", rownames(seuratObj_LiveCells_global@data), value = TRUE)
percent.mito <- colSums(as.matrix(expm1(seuratObj_LiveCells_global@data[mito.genes, ]))) / colSums(as.matrix(expm1(seuratObj_LiveCells_global@data)))
seuratObj_LiveCells_global <- AddMetaData(seuratObj_LiveCells_global, percent.mito, 'percent.mito')
GenePlot(seuratObj_LiveCells_global, 'nUMI', 'percent.mito')
GenePlot(seuratObj_LiveCells_global, 'nUMI', 'nGene')
#- remove unwanted sources of variation
seuratObj_LiveCells_global <- RegressOut(seuratObj_LiveCells_global, latent.vars = c('nUMI', 'percent.mito')) # remove effect of CDR (high correlation between nGene and nUMI - 0.97) and mitochondrial
```

```{r echo=FALSE, eval=TRUE}
seuratObj_LiveCells_global <- MeanVarPlot(seuratObj_LiveCells_global, fxn.x = expMean, fxn.y = logVarDivMean, x.low.cutoff = 0.25, x.high.cutoff = 3, y.cutoff = 0.5, do.contour = FALSE)
length(seuratObj_LiveCells_global@var.genes)
```

```{r echo=FALSE, eval=TRUE}
module <- "BTM"
min_gene_in_module <- 5
packageExt <- system.file("extdata", package='MAST')
module_file <- list.files(packageExt, pattern = module, full.names = TRUE)
gene_set <- getGmt(module_file)
gene_ids <- geneIds(gene_set)
```

```{r echo=FALSE, eval=TRUE}
vec <- seuratObj_LiveCells_global@mean.var$data.norm.y
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE)[1:20],]
```



## TFH041

### TFH sorted cells


```{r echo=FALSE, eval=TRUE}
seuratObj_TFH_global <- get(load("../output/TFH041/seuratTFH.rda"))
```

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
###--- Regress out unwanted sources of variation
mito.genes <- grep("^MT-", rownames(seuratObj_TFH_global@data), value = TRUE)
percent.mito <- colSums(as.matrix(expm1(seuratObj_TFH_global@data[mito.genes, ]))) / colSums(as.matrix(expm1(seuratObj_TFH_global@data)))
seuratObj_TFH_global <- AddMetaData(seuratObj_TFH_global, percent.mito, 'percent.mito')
GenePlot(seuratObj_TFH_global, 'nUMI', 'percent.mito')
GenePlot(seuratObj_TFH_global, 'nUMI', 'nGene')
#- remove unwanted sources of variation
seuratObj_TFH_global <- RegressOut(seuratObj_TFH_global, latent.vars = c('nUMI', 'percent.mito')) # remove effect of CDR (high correlation between nGene and nUMI - 0.97) and mitochondrial
```


```{r echo=FALSE, eval=TRUE}
seuratObj_TFH_global <- MeanVarPlot(seuratObj_TFH_global, fxn.x = expMean, fxn.y = logVarDivMean, x.low.cutoff = 0.25, x.high.cutoff = 3, y.cutoff = 0.5, do.contour = FALSE)
length(seuratObj_TFH_global@var.genes)
```

Pathway analysis of the normed mean variance measure calculated from Seurat.

```{r echo=FALSE, eval=TRUE}
module <- "BTM"
min_gene_in_module <- 5
packageExt <- system.file("extdata", package='MAST')
module_file <- list.files(packageExt, pattern = module, full.names = TRUE)
gene_set <- getGmt(module_file)
gene_ids <- geneIds(gene_set)
```

```{r echo=FALSE, eval=TRUE}
vec <- seuratObj_TFH_global@mean.var$data.norm.y
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE)[1:20],]
```

### Live Cells

```{r echo=FALSE, eval=TRUE}
seuratObj_LiveCells_global <- get(load("../output/TFH041/seuratLiveCells.rda"))
```

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
###--- Regress out unwanted sources of variation
mito.genes <- grep("^MT-", rownames(seuratObj_LiveCells_global@data), value = TRUE)
percent.mito <- colSums(as.matrix(expm1(seuratObj_LiveCells_global@data[mito.genes, ]))) / colSums(as.matrix(expm1(seuratObj_LiveCells_global@data)))
seuratObj_LiveCells_global <- AddMetaData(seuratObj_LiveCells_global, percent.mito, 'percent.mito')
GenePlot(seuratObj_LiveCells_global, 'nUMI', 'percent.mito')
GenePlot(seuratObj_LiveCells_global, 'nUMI', 'nGene')
#- remove unwanted sources of variation
seuratObj_LiveCells_global <- RegressOut(seuratObj_LiveCells_global, latent.vars = c('nUMI', 'percent.mito')) # remove effect of CDR (high correlation between nGene and nUMI - 0.97) and mitochondrial
```

```{r echo=FALSE, eval=TRUE}
seuratObj_LiveCells_global <- MeanVarPlot(seuratObj_LiveCells_global, fxn.x = expMean, fxn.y = logVarDivMean, x.low.cutoff = 0.25, x.high.cutoff = 3, y.cutoff = 0.5, do.contour = FALSE)
length(seuratObj_LiveCells_global@var.genes)
```

```{r echo=FALSE, eval=TRUE}
module <- "BTM"
min_gene_in_module <- 5
packageExt <- system.file("extdata", package='MAST')
module_file <- list.files(packageExt, pattern = module, full.names = TRUE)
gene_set <- getGmt(module_file)
gene_ids <- geneIds(gene_set)
```

```{r echo=FALSE, eval=TRUE}
vec <- seuratObj_LiveCells_global@mean.var$data.norm.y
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE)[1:20],]
```


