---
title: "Skeleton of distrom"
author: "Kushal K Dey"
date: "9/7/2017"
output: html_document
---

In this script, we investigate the skeleton of the **distrom** package and try to see what happens inside the *dmr* function of this package. We take the Himalayan bird abundance data as the test data for this case.

```{r}
library(ecostructure)
library(covtpx)
library(Biobase)
library(distrom)
library(Seurat)
```

```{r}
data <- get(load(system.file("extdata", "HimalayanBirdsData.rda", package = "ecostructure")))
taxonomic_counts <- t(exprs(data))
grid_metadata <- pData(phenoData(data))
covars1 <- grid_metadata[,1:3]
covars2 <- model.matrix(~ factor(grid_metadata$WorE)-1)
covars <- cbind(covars1, covars2)
```

Set up the cluster with number of cores same as that in my machine.

```{r}
cl <- makeCluster(parallel::detectCores(),type=ifelse(.Platform$OS.type=="unix","FORK","PSOCK"))
print(cl)
```


Create an argument list `argl` 
```{r}
mu <- rep(0, dim(taxonomic_counts)[1])
bins=NULL
verb=0
cv=FALSE
argl <- list()
argl$family <- "poisson"
if(is.null(argl$nlambda))
    argl$nlambda <- formals(gamlr)$nlambda
argl$verb <- max(verb-1,0)
argl$cv <- cv
```

```{r}
source("../../distrom/R/collapse.R")
```

```{r}
chk <- collapse(covars[,1:3], taxonomic_counts, mu, bins)
```

`chk` is a list with `v` attribute corresponding to the metadata, a `counts` attribute comprising of the counts data in sparse format, `nbins` set as 1 as no collapse, `mu` representing the intercept to be added. if NULL, then log(rowSums) used.

```{r}
cat(sprintf("fitting %d observations on %d categories, %d covariates.\n",
    nrow(chk$v), ncol(chk$counts), ncol(chk$v)))
```

Add the metadata and the mean shift to argument list.

```{r}
argl$x <- chk$v
argl$shift <- chk$mu
```

Report the number of columns and the column names.

```{r}
p <- ncol(chk$counts)
vars <- colnames(chk$counts)
```

```{r}
rownames(argl$x) <- rownames(chk$counts) <- NULL
counts <- chk$counts
rm(covars,mu,chk)
taxo_counts <- counts
```


```{r}
C <- ifelse(is.null(cl),Inf,length(cl))
```


```{r}
if(C < p/4){
    chunks <- round(seq(0,p,length.out=C+1))
    counts <- lapply(1:C, 
      function(i) counts[,(chunks[i]+1):chunks[i+1]])
    counts <- parLapply(cl,
                counts, 
                function(x) 
                  sapply(colnames(x), 
                  function(j) x[,j,drop=FALSE]))
    counts <- unlist(counts,recursive=FALSE)
  } else{
    counts <- sapply(vars,
      function(j) counts[,j,drop=FALSE]) }

```

```{r}
onerun <- function(xj, argl){
  if(length(xj@i)==0) return(NULL) # n'er occurs
  argl$y <- xj
  if(argl$cv) fit <- do.call(cv.gamlr,argl)
  else fit <- do.call(gamlr,argl)
  return(fit)
}
```

```{r}
mods <- parLapply(cl,counts,onerun,argl=argl) 
```

Define a class to store the output.

```{r}
class(mods) <- "dmr"
attr(mods,"nobs") <- argl$nobs
attr(mods,"nlambda") <- argl$nlambda
attr(mods,"mu") <- argl$shift
```

