---
title: 'Bird data : application of distrom'
author: "Kushal K Dey"
date: "9/7/2017"
output: html_document
---

In this script, we perform distrom on the birds data and see the performance of the method and how it treats the known sources of variation like elevation of the ranges, East-West directional influence on the bird patterns.

## Data Processing

```{r echo=TRUE, eval=TRUE, message = FALSE, warning=FALSE}
library(ecostructure)
library(covtpx)
library(Biobase)
library(distrom)
library(Seurat)
```

Loading the counts data 

```{r}
data <- get(load(system.file("extdata", "HimalayanBirdsData.rda", package = "ecostructure")))
taxonomic_counts <- t(exprs(data))
grid_metadata <- pData(phenoData(data))
```

```{r}
covars1 <- grid_metadata[,1:3]
covars2 <- model.matrix(~ factor(grid_metadata$WorE)-1)
covars <- cbind(covars1, covars2)
```


## distrom

```{r}
cl <- makeCluster(parallel::detectCores(),type=ifelse(.Platform$OS.type=="unix","FORK","PSOCK"))
print(cl)
system.time(fits <- dmr(cl, covars[,1:3], taxonomic_counts+1, verb=1))
stopCluster(cl)
```

```{r}
coef(fits)
```
```{r}
coefs_birds <- as.matrix(coef(fits))
```

### Elevation Driving Birds

Top elevation driving birds

```{r echo=FALSE}
imp_birds <- names(sort(abs(coefs_birds[2,]), decreasing =TRUE))[1:5]
```


```{r echo=FALSE}
data_ggplot <- data.frame(Meta = grid_metadata$Elevation,
                          First = taxonomic_counts[, paste0(imp_birds[1])], 
                          Second = taxonomic_counts[, paste0(imp_birds[2])],
                          Third = taxonomic_counts[, paste0(imp_birds[3])], 
                          Fourth = taxonomic_counts[, paste0(imp_birds[4])],
                          Fifth = taxonomic_counts[, paste0(imp_birds[5])]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = First), size = 1) + labs(x = 'Elevation', y = 'abundance', title = paste0(imp_birds[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Second), size = 1) + labs(x = 'Elevation', y = 'abundance', title = paste0(imp_birds[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Third), size = 1) + labs(x = 'Elevation', y = 'abundance', title = paste0(imp_birds[3]))


plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fourth), size = 1) + labs(x = 'Elevation', y = 'abundance', title = paste0(imp_birds[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fifth), size = 1) + labs(x = 'Elevation', y = 'abundance', title = paste0(imp_birds[5]))

plot_grid(plot1, plot2, plot3, plot4, plot5, ncol = 2, align = 'v')
```

### North/South Driving Birds

```{r echo=FALSE}
imp_birds <- names(sort(abs(coefs_birds[3,]), decreasing =TRUE))[1:5]
sort(abs(coefs_birds[3,]), decreasing =TRUE)[1:5]
```


```{r echo=FALSE}
data_ggplot <- data.frame(Meta = grid_metadata$North,
                          First = taxonomic_counts[, paste0(imp_birds[1])], 
                          Second = taxonomic_counts[, paste0(imp_birds[2])],
                          Third = taxonomic_counts[, paste0(imp_birds[3])], 
                          Fourth = taxonomic_counts[, paste0(imp_birds[4])],
                          Fifth = taxonomic_counts[, paste0(imp_birds[5])]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = First), size = 1) + labs(x = 'North', y = 'abundance', title = paste0(imp_birds[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Second), size = 1) + labs(x = 'North', y = 'abundance', title = paste0(imp_birds[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Third), size = 1) + labs(x = 'North', y = 'abundance', title = paste0(imp_birds[3]))


plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fourth), size = 1) + labs(x = 'North', y = 'abundance', title = paste0(imp_birds[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fifth), size = 1) + labs(x = 'North', y = 'abundance', title = paste0(imp_birds[5]))

plot_grid(plot1, plot2, plot3, plot4, plot5, ncol = 2, align = 'v')

```


### East/West Driving Birds

```{r echo=FALSE}
imp_birds <- names(sort(abs(coefs_birds[4,]), decreasing =TRUE))[1:5]
sort(abs(coefs_birds[4,]), decreasing =TRUE)[1:5]
```


```{r echo=FALSE}
data_ggplot <- data.frame(Meta = grid_metadata$East,
                          First = taxonomic_counts[, paste0(imp_birds[1])], 
                          Second = taxonomic_counts[, paste0(imp_birds[2])],
                          Third = taxonomic_counts[, paste0(imp_birds[3])], 
                          Fourth = taxonomic_counts[, paste0(imp_birds[4])],
                          Fifth = taxonomic_counts[, paste0(imp_birds[5])]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = First), size = 1) + labs(x = 'East', y = 'abundance', title = paste0(imp_birds[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Second), size = 1) + labs(x = 'East', y = 'abundance', title = paste0(imp_birds[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Third), size = 1) + labs(x = 'East', y = 'abundance', title = paste0(imp_birds[3]))


plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fourth), size = 1) + labs(x = 'East', y = 'abundance', title = paste0(imp_birds[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fifth), size = 1) + labs(x = 'East', y = 'abundance', title = paste0(imp_birds[5]))

plot_grid(plot1, plot2, plot3, plot4, plot5, ncol = 2, align = 'v')

```

We check now whether the distrom model found bird species match with a simpler linear model fit.


## Linear Model

```{r}
coef_mat <- matrix(0, 3, dim(taxonomic_counts)[2])
for(m in 1:dim(taxonomic_counts)[2]){
  out <- lm(log(taxonomic_counts[,m]+1) ~ covars[,1] + covars[,2] + covars[,3])
  coef_mat[, m] <- summary(out)$coefficients[-1,3]
}
rownames(coef_mat) <- c("Elevation", "North", "East")
colnames(coef_mat) <- colnames(taxonomic_counts)
```

### Elevation Driving Birds

Top elevation driving birds

```{r echo=FALSE}
imp_birds <- names(sort(abs(coef_mat[1,]), decreasing =TRUE))[1:10]
```


```{r echo=FALSE}
data_ggplot <- data.frame(Meta = grid_metadata$Elevation,
                          First = taxonomic_counts[, paste0(imp_birds[1])], 
                          Second = taxonomic_counts[, paste0(imp_birds[2])],
                          Third = taxonomic_counts[, paste0(imp_birds[3])], 
                          Fourth = taxonomic_counts[, paste0(imp_birds[4])],
                          Fifth = taxonomic_counts[, paste0(imp_birds[5])]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = First), size = 1) + labs(x = 'Elevation', y = 'abundance', title = paste0(imp_birds[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Second), size = 1) + labs(x = 'Elevation', y = 'abundance', title = paste0(imp_birds[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Third), size = 1) + labs(x = 'Elevation', y = 'abundance', title = paste0(imp_birds[3]))


plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fourth), size = 1) + labs(x = 'Elevation', y = 'abundance', title = paste0(imp_birds[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fifth), size = 1) + labs(x = 'Elevation', y = 'abundance', title = paste0(imp_birds[5]))

plot_grid(plot1, plot2, plot3, plot4, plot5, ncol = 2, align = 'v')

```


### East/West Driving Birds

```{r echo=FALSE}
imp_birds <- names(sort(abs(coef_mat[3,]), decreasing =TRUE))[1:5]
sort(abs(coefs_birds[3,]), decreasing =TRUE)[1:5]
```


```{r echo=FALSE}
data_ggplot <- data.frame(Meta = grid_metadata$East,
                          First = taxonomic_counts[, paste0(imp_birds[1])], 
                          Second = taxonomic_counts[, paste0(imp_birds[2])],
                          Third = taxonomic_counts[, paste0(imp_birds[3])], 
                          Fourth = taxonomic_counts[, paste0(imp_birds[4])],
                          Fifth = taxonomic_counts[, paste0(imp_birds[5])]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = First), size = 1) + labs(x = 'East', y = 'abundance', title = paste0(imp_birds[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Second), size = 1) + labs(x = 'East', y = 'abundance', title = paste0(imp_birds[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Third), size = 1) + labs(x = 'East', y = 'abundance', title = paste0(imp_birds[3]))


plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fourth), size = 1) + labs(x = 'East', y = 'abundance', title = paste0(imp_birds[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fifth), size = 1) + labs(x = 'East', y = 'abundance', title = paste0(imp_birds[5]))

plot_grid(plot1, plot2, plot3, plot4, plot5, ncol = 2, align = 'v')

```


### North/South Driving Birds

```{r echo=FALSE}
imp_birds <- names(sort(abs(coef_mat[2,]), decreasing =TRUE))[1:5]
sort(abs(coef_mat[2,]), decreasing =TRUE)[1:5]
```


```{r echo=FALSE}
data_ggplot <- data.frame(Meta = grid_metadata$North,
                          First = taxonomic_counts[, paste0(imp_birds[1])], 
                          Second = taxonomic_counts[, paste0(imp_birds[2])],
                          Third = taxonomic_counts[, paste0(imp_birds[3])], 
                          Fourth = taxonomic_counts[, paste0(imp_birds[4])],
                          Fifth = taxonomic_counts[, paste0(imp_birds[5])]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = First), size = 1) + labs(x = 'North', y = 'abundance', title = paste0(imp_birds[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Second), size = 1) + labs(x = 'North', y = 'abundance', title = paste0(imp_birds[2]))

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Third), size = 1) + labs(x = 'North', y = 'abundance', title = paste0(imp_birds[3]))


plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fourth), size = 1) + labs(x = 'North', y = 'abundance', title = paste0(imp_birds[4]))

plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1),                                      panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = Meta, y = Fifth), size = 1) + labs(x = 'North', y = 'abundance', title = paste0(imp_birds[5]))

plot_grid(plot1, plot2, plot3, plot4, plot5, ncol = 2, align = 'v')

```


