---
title: 'Gene Set Enrichment analysis : MCC1050 data'
author: "Kushal K Dey"
date: "8/10/2017"
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(Seurat)
library(plyr)
library(dplyr)
library(Matrix)
library(cowplot)
library(stringr)
library(MAST)
library(doMC)
library(pheatmap)
library(grid)
library(stringr)
library(CountClust)
```

We perform gene set enrichment analysis of the driving genes in the HIV dataset.

```{r echo=FALSE, eval=TRUE}
seuratObj_TFH_global <- get(load("../output/seurat_MCCB1050.rda"))
```

Countlust output.

```{r}
topic_clus <- get(load("../output/maptpx_GS_PBMC_8_2013_MCCB1050.rda"))
```

```{r}
indices <- ExtractTopFeatures(topic_clus[[2]]$theta, top_features = 50, method = "poisson", options = "max")
imp_genes <- apply(indices, 1, function(x) return(rownames(topic_clus[[2]]$theta)[x]))
```

We save the results 

```{r echo=FALSE, eval=TRUE}
for(l in 1:dim(imp_genes)[2]){
  write.table(imp_genes[,l], quote = FALSE, file = paste0("../utilities/MCC1050/cluster_2/gene_names_clus_", l, ".txt"), row.names = FALSE, col.names = FALSE)
}
```

## MCC1050 - [K=2]


### pathway analysis (cluster 1)


```{r echo=FALSE, eval=TRUE}
l <- 1
pathway2 <- read.delim(paste0("../utilities/MCC1050/cluster_2/gene_names_clus_", l, ".tab"))
head(pathway2$pathway, 10)

if(length(which(pathway2$q.value < 0.005)) > 2){
  pathway2 <- pathway2[which(pathway2$q.value < 0.005),]
}
maxpath <- 75
pathway <- pathway2[1:min(maxpath, dim(pathway2)[1]), ]
ensembl_genes <- pathway$members_input_overlap
pathway_list_genes <- sapply(ensembl_genes, function(x) return(strsplit(as.character(x), "; ")))
all_genes <- Reduce(union, pathway_list_genes)
pathway_mat <- matrix(0, length(pathway_list_genes), length(all_genes))
for(l in 1:dim(pathway_mat)[1]){
  pathway_mat[l, match(pathway_list_genes[[l]], all_genes)] <- 1
}

pathway_bimat <- (pathway_mat)%*%t(pathway_mat)
pathway_bimat_prop <- diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1]) %*% pathway_bimat %*% diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1])

col=c(rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)))
heatmap(pathway_bimat_prop, labRow = pathway$pathway, labCol = pathway$pathway, cexRow = 0.3, cexCol = 0.3, col = col, zlim = c(-1,1),
        scale = "none", margins = c(5, 5))

```

### pathway analysis (cluster 2)


```{r echo=FALSE, eval=TRUE}
l <- 2
pathway2 <- read.delim(paste0("../utilities/MCC1050/cluster_2/gene_names_clus_", l, ".tab"))
head(pathway2$pathway, 10)

if(length(which(pathway2$q.value < 0.005)) > 2){
  pathway2 <- pathway2[which(pathway2$q.value < 0.005),]
}
maxpath <- 75
pathway <- pathway2[1:min(maxpath, dim(pathway2)[1]), ]
ensembl_genes <- pathway$members_input_overlap
pathway_list_genes <- sapply(ensembl_genes, function(x) return(strsplit(as.character(x), "; ")))
all_genes <- Reduce(union, pathway_list_genes)
pathway_mat <- matrix(0, length(pathway_list_genes), length(all_genes))
for(l in 1:dim(pathway_mat)[1]){
  pathway_mat[l, match(pathway_list_genes[[l]], all_genes)] <- 1
}

pathway_bimat <- (pathway_mat)%*%t(pathway_mat)
pathway_bimat_prop <- diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1]) %*% pathway_bimat %*% diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1])

col=c(rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)))
heatmap(pathway_bimat_prop, labRow = pathway$pathway, labCol = pathway$pathway, cexRow = 0.3, cexCol = 0.3, col = col, zlim = c(-1,1),
        scale = "none", margins = c(5, 5))

```




## MCC1050 - [K=3]

```{r}
indices <- ExtractTopFeatures(topic_clus[[3]]$theta, top_features = 50, method = "poisson", options = "max")
imp_genes <- apply(indices, 1, function(x) return(rownames(topic_clus[[3]]$theta)[x]))
```

We save the results 

```{r echo=FALSE, eval=TRUE}
for(l in 1:dim(imp_genes)[2]){
  write.table(imp_genes[,l], quote = FALSE, file = paste0("../utilities/MCC1050/cluster_3/gene_names_clus_", l, ".txt"), row.names = FALSE, col.names = FALSE)
}
```

### pathway analysis (cluster 1)


```{r echo=FALSE, eval=TRUE}
l <- 1
pathway2 <- read.delim(paste0("../utilities/MCC1050/cluster_3/gene_names_clus_", l, ".tab"))
head(pathway2$pathway, 10)

if(length(which(pathway2$q.value < 0.005)) > 2){
  pathway2 <- pathway2[which(pathway2$q.value < 0.005),]
}
maxpath <- 75
pathway <- pathway2[1:min(maxpath, dim(pathway2)[1]), ]
ensembl_genes <- pathway$members_input_overlap
pathway_list_genes <- sapply(ensembl_genes, function(x) return(strsplit(as.character(x), "; ")))
all_genes <- Reduce(union, pathway_list_genes)
pathway_mat <- matrix(0, length(pathway_list_genes), length(all_genes))
for(l in 1:dim(pathway_mat)[1]){
  pathway_mat[l, match(pathway_list_genes[[l]], all_genes)] <- 1
}

pathway_bimat <- (pathway_mat)%*%t(pathway_mat)
pathway_bimat_prop <- diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1]) %*% pathway_bimat %*% diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1])

col=c(rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)))
heatmap(pathway_bimat_prop, labRow = pathway$pathway, labCol = pathway$pathway, cexRow = 0.3, cexCol = 0.3, col = col, zlim = c(-1,1),
        scale = "none", margins = c(5, 5))

```

### pathway analysis (cluster 2)


```{r echo=FALSE,eval=TRUE}
l <- 2
pathway2 <- read.delim(paste0("../utilities/MCC1050/cluster_3/gene_names_clus_", l, ".tab"))
head(pathway2$pathway, 10)

if(length(which(pathway2$q.value < 0.005)) > 2){
  pathway2 <- pathway2[which(pathway2$q.value < 0.005),]
}
maxpath <- 75
pathway <- pathway2[1:min(maxpath, dim(pathway2)[1]), ]
ensembl_genes <- pathway$members_input_overlap
pathway_list_genes <- sapply(ensembl_genes, function(x) return(strsplit(as.character(x), "; ")))
all_genes <- Reduce(union, pathway_list_genes)
pathway_mat <- matrix(0, length(pathway_list_genes), length(all_genes))
for(l in 1:dim(pathway_mat)[1]){
  pathway_mat[l, match(pathway_list_genes[[l]], all_genes)] <- 1
}

pathway_bimat <- (pathway_mat)%*%t(pathway_mat)
pathway_bimat_prop <- diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1]) %*% pathway_bimat %*% diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1])

col=c(rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)))
heatmap(pathway_bimat_prop, labRow = pathway$pathway, labCol = pathway$pathway, cexRow = 0.3, cexCol = 0.3, col = col, zlim = c(-1,1),
        scale = "none", margins = c(5, 5))

```


### pathway analysis (cluster 3)


```{r eco=FALSE, eval=TRUE}
l <- 3
pathway2 <- read.delim(paste0("../utilities/MCC1050/cluster_3/gene_names_clus_", l, ".tab"))
head(pathway2$pathway, 10)

if(length(which(pathway2$q.value < 0.005)) > 2){
  pathway2 <- pathway2[which(pathway2$q.value < 0.005),]
}
maxpath <- 75
pathway <- pathway2[1:min(maxpath, dim(pathway2)[1]), ]
ensembl_genes <- pathway$members_input_overlap
pathway_list_genes <- sapply(ensembl_genes, function(x) return(strsplit(as.character(x), "; ")))
all_genes <- Reduce(union, pathway_list_genes)
pathway_mat <- matrix(0, length(pathway_list_genes), length(all_genes))
for(l in 1:dim(pathway_mat)[1]){
  pathway_mat[l, match(pathway_list_genes[[l]], all_genes)] <- 1
}

pathway_bimat <- (pathway_mat)%*%t(pathway_mat)
pathway_bimat_prop <- diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1]) %*% pathway_bimat %*% diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1])

col=c(rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)))
heatmap(pathway_bimat_prop, labRow = pathway$pathway, labCol = pathway$pathway, cexRow = 0.3, cexCol = 0.3, col = col, zlim = c(-1,1),
        scale = "none", margins = c(5, 5))

```




## MCC1050 - [K=6]

```{r}
indices <- ExtractTopFeatures(topic_clus[[6]]$theta, top_features = 50, method = "poisson", options = "max")
imp_genes <- apply(indices, 1, function(x) return(rownames(topic_clus[[6]]$theta)[x]))
```

We save the results 

```{r echo=FALSE, eval=TRUE}
for(l in 1:dim(imp_genes)[2]){
  write.table(imp_genes[,l], quote = FALSE, file = paste0("../utilities/MCC1050/cluster_6/gene_names_clus_", l, ".txt"), row.names = FALSE, col.names = FALSE)
}
```

### pathway analysis (cluster 1)


```{r echo=FALSE, eval=TRUE}
l <- 1
pathway2 <- read.delim(paste0("../utilities/MCC1050/cluster_6/gene_names_clus_", l, ".tab"))
head(pathway2$pathway, 10)

if(length(which(pathway2$q.value < 0.005)) > 2){
  pathway2 <- pathway2[which(pathway2$q.value < 0.005),]
}
maxpath <- 75
pathway <- pathway2[1:min(maxpath, dim(pathway2)[1]), ]
ensembl_genes <- pathway$members_input_overlap
pathway_list_genes <- sapply(ensembl_genes, function(x) return(strsplit(as.character(x), "; ")))
all_genes <- Reduce(union, pathway_list_genes)
pathway_mat <- matrix(0, length(pathway_list_genes), length(all_genes))
for(l in 1:dim(pathway_mat)[1]){
  pathway_mat[l, match(pathway_list_genes[[l]], all_genes)] <- 1
}

pathway_bimat <- (pathway_mat)%*%t(pathway_mat)
pathway_bimat_prop <- diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1]) %*% pathway_bimat %*% diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1])

col=c(rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)))
heatmap(pathway_bimat_prop, labRow = pathway$pathway, labCol = pathway$pathway, cexRow = 0.3, cexCol = 0.3, col = col, zlim = c(-1,1),
        scale = "none", margins = c(5, 5))

```

### pathway analysis (cluster 2)


```{r echo=FALSE, eval=TRUE}
l <- 2
pathway2 <- read.delim(paste0("../utilities/MCC1050/cluster_6/gene_names_clus_", l, ".tab"))
head(pathway2$pathway, 10)

if(length(which(pathway2$q.value < 0.005)) > 2){
  pathway2 <- pathway2[which(pathway2$q.value < 0.005),]
}
maxpath <- 75
pathway <- pathway2[1:min(maxpath, dim(pathway2)[1]), ]
ensembl_genes <- pathway$members_input_overlap
pathway_list_genes <- sapply(ensembl_genes, function(x) return(strsplit(as.character(x), "; ")))
all_genes <- Reduce(union, pathway_list_genes)
pathway_mat <- matrix(0, length(pathway_list_genes), length(all_genes))
for(l in 1:dim(pathway_mat)[1]){
  pathway_mat[l, match(pathway_list_genes[[l]], all_genes)] <- 1
}

pathway_bimat <- (pathway_mat)%*%t(pathway_mat)
pathway_bimat_prop <- diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1]) %*% pathway_bimat %*% diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1])

col=c(rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)))
heatmap(pathway_bimat_prop, labRow = pathway$pathway, labCol = pathway$pathway, cexRow = 0.3, cexCol = 0.3, col = col, zlim = c(-1,1),
        scale = "none", margins = c(5, 5))

```


### pathway analysis (cluster 3)


```{r echo=FALSE, eval=TRUE}
l <- 3
pathway2 <- read.delim(paste0("../utilities/MCC1050/cluster_6/gene_names_clus_", l, ".tab"))
head(pathway2$pathway, 10)

if(length(which(pathway2$q.value < 0.005)) > 2){
  pathway2 <- pathway2[which(pathway2$q.value < 0.005),]
}
maxpath <- 75
pathway <- pathway2[1:min(maxpath, dim(pathway2)[1]), ]
ensembl_genes <- pathway$members_input_overlap
pathway_list_genes <- sapply(ensembl_genes, function(x) return(strsplit(as.character(x), "; ")))
all_genes <- Reduce(union, pathway_list_genes)
pathway_mat <- matrix(0, length(pathway_list_genes), length(all_genes))
for(l in 1:dim(pathway_mat)[1]){
  pathway_mat[l, match(pathway_list_genes[[l]], all_genes)] <- 1
}

pathway_bimat <- (pathway_mat)%*%t(pathway_mat)
pathway_bimat_prop <- diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1]) %*% pathway_bimat %*% diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1])

col=c(rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)))
heatmap(pathway_bimat_prop, labRow = pathway$pathway, labCol = pathway$pathway, cexRow = 0.3, cexCol = 0.3, col = col, zlim = c(-1,1),
        scale = "none", margins = c(5, 5))

```


### pathway analysis (cluster 4)


```{r echo=FALSE, eval=TRUE}
l <- 4
pathway2 <- read.delim(paste0("../utilities/MCC1050/cluster_6/gene_names_clus_", l, ".tab"))
head(pathway2$pathway, 10)

if(length(which(pathway2$q.value < 0.005)) > 2){
  pathway2 <- pathway2[which(pathway2$q.value < 0.005),]
}
maxpath <- 75
pathway <- pathway2[1:min(maxpath, dim(pathway2)[1]), ]
ensembl_genes <- pathway$members_input_overlap
pathway_list_genes <- sapply(ensembl_genes, function(x) return(strsplit(as.character(x), "; ")))
all_genes <- Reduce(union, pathway_list_genes)
pathway_mat <- matrix(0, length(pathway_list_genes), length(all_genes))
for(l in 1:dim(pathway_mat)[1]){
  pathway_mat[l, match(pathway_list_genes[[l]], all_genes)] <- 1
}

pathway_bimat <- (pathway_mat)%*%t(pathway_mat)
pathway_bimat_prop <- diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1]) %*% pathway_bimat %*% diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1])

col=c(rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)))
heatmap(pathway_bimat_prop, labRow = pathway$pathway, labCol = pathway$pathway, cexRow = 0.3, cexCol = 0.3, col = col, zlim = c(-1,1),
        scale = "none", margins = c(5, 5))

```


### pathway analysis (cluster 5)


```{r echo=FALSE, eval=TRUE}
l <- 5
pathway2 <- read.delim(paste0("../utilities/MCC1050/cluster_6/gene_names_clus_", l, ".tab"))
head(pathway2$pathway, 10)

if(length(which(pathway2$q.value < 0.005)) > 2){
  pathway2 <- pathway2[which(pathway2$q.value < 0.005),]
}
maxpath <- 75
pathway <- pathway2[1:min(maxpath, dim(pathway2)[1]), ]
ensembl_genes <- pathway$members_input_overlap
pathway_list_genes <- sapply(ensembl_genes, function(x) return(strsplit(as.character(x), "; ")))
all_genes <- Reduce(union, pathway_list_genes)
pathway_mat <- matrix(0, length(pathway_list_genes), length(all_genes))
for(l in 1:dim(pathway_mat)[1]){
  pathway_mat[l, match(pathway_list_genes[[l]], all_genes)] <- 1
}

pathway_bimat <- (pathway_mat)%*%t(pathway_mat)
pathway_bimat_prop <- diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1]) %*% pathway_bimat %*% diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1])

col=c(rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)))
heatmap(pathway_bimat_prop, labRow = pathway$pathway, labCol = pathway$pathway, cexRow = 0.3, cexCol = 0.3, col = col, zlim = c(-1,1),
        scale = "none", margins = c(5, 5))

```


### pathway analysis (cluster 6)


```{r echo=FALSE, eval=TRUE}
l <- 6
pathway2 <- read.delim(paste0("../utilities/MCC1050/cluster_6/gene_names_clus_", l, ".tab"))
head(pathway2$pathway, 10)

if(length(which(pathway2$q.value < 0.005)) > 2){
  pathway2 <- pathway2[which(pathway2$q.value < 0.005),]
}
maxpath <- 75
pathway <- pathway2[1:min(maxpath, dim(pathway2)[1]), ]
ensembl_genes <- pathway$members_input_overlap
pathway_list_genes <- sapply(ensembl_genes, function(x) return(strsplit(as.character(x), "; ")))
all_genes <- Reduce(union, pathway_list_genes)
pathway_mat <- matrix(0, length(pathway_list_genes), length(all_genes))
for(l in 1:dim(pathway_mat)[1]){
  pathway_mat[l, match(pathway_list_genes[[l]], all_genes)] <- 1
}

pathway_bimat <- (pathway_mat)%*%t(pathway_mat)
pathway_bimat_prop <- diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1]) %*% pathway_bimat %*% diag(1/sqrt(diag(pathway_bimat)), dim(pathway_bimat)[1])

col=c(rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)))
heatmap(pathway_bimat_prop, labRow = pathway$pathway, labCol = pathway$pathway, cexRow = 0.3, cexCol = 0.3, col = col, zlim = c(-1,1),
        scale = "none", margins = c(5, 5))

```
