---
title: "Jurkat + 293T cells (99-1 mix)"
author: "Kushal K Dey"
date: "9/24/2017"
output: html_document
---

We take a mixture of $99\%$ mixture of Jurkat cells and $1\%$ 293T cells. 
We aim to perform unsupervised Countclust clustering of the cells to see 
if the clusters picked up in an unsupervised way correspond to the Jurkat cells and 293T cells. 

```{r message = FALSE, warning=FALSE}
library(cellrangerRkit)
```

```{r message=FALSE, warning = FALSE}
library(CountClust)
library(maptpx)
library(ggplot2)
library(MAST)
library(GSEABase)
library(Seurat)
library(classtpx)
```

```{r}
data <- Read10X("../data/jurkat_293T_99_1/filtered_matrices_mex/hg19/")
```

The dimensionality of the matrix loaded

```{r}
dim(data)
```


We first remove all the ribosomal, mitochondrial, small RNA genes reported in the above data matrix.

We report the sample names

```{r}
colnames(data)[1:10]
```

We report the names of the genes 

```{r}
rownames(data)[1:10]
```


```{r}
idx2 <- which(!is.na(match(substring(rownames(data), 1, 2), c("RP", "MT", "RN"))))
```

```{r}
data2 <- data[-idx2, ]
```

Remove data from multiple gene mapping and small RNA.

```{r}
idx3 <- grep("[.]", rownames(data2))
idx4 <- grep("[-]", rownames(data2))
```

```{r}
data3 <- data2[-union(idx3, idx4), ]
```

We now create a Seurat object using this data matrix.

```{r}
seuratObj <- new('seurat', raw.data = data3)
seuratObj <- Setup(seuratObj, min.cells = 0, min.genes = 0, project = 'Pantaleo', total.expr = 10000) # no need to filter - already done
#- Output
seuratObj_TFH_global <- seuratObj
```

```{r}
seuratObj_TFH_global <- MeanVarPlot(seuratObj_TFH_global, fxn.x = expMean, fxn.y = logVarDivMean, x.low.cutoff = 0.25, x.high.cutoff = 3, y.cutoff = 0.5, do.contour = FALSE)
length(seuratObj_TFH_global@var.genes)
seuratObj_TFH_global <- PCA(seuratObj_TFH_global, pc.genes = seuratObj_TFH_global@var.genes)
seuratObj_TFH_global <- ProjectPCA(seuratObj_TFH_global)
VizPCA(seuratObj_TFH_global, 1:2)
```

```{r echo=FALSE, eval=FALSE}
seuratObj_TFH_global <- RunTSNE(seuratObj_TFH_global, dims.use = 1:10, perplexity = 50)
```

```{r echo=FALSE, eval=FALSE}
save(seuratObj_TFH_global, file = "../output/seurat_jurkat_293T_99_1.rda")
```

## Mixture (Jurkat + 293T) data Processing and Visualization

```{r echo=FALSE, eval=TRUE}
seuratObj_TFH_global <- get(load("../output/seurat_jurkat_293T_99_1.rda"))
fac <- rep("jurkat_293T", dim(seuratObj_TFH_global@data)[2])
```

## t-SNE projection

```{r echo=FALSE, eval=TRUE}
labels <- fac
nUMI <- seuratObj_TFH_global@data.info$nUMI
nGene <- seuratObj_TFH_global@data.info$nGene

data_ggplot <- data.frame(labels = labels,
                          nUMI = nUMI,
                          nGene = nGene,
                          tSNE_1 = seuratObj_TFH_global@tsne.rot[, 1],
                          tSNE_2 = seuratObj_TFH_global@tsne.rot[, 2])

```


```{r echo=FALSE, eval=TRUE}
plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```
## Jurkat + 293T sorted Data processing

We load the Jurkat cells data.

```{r}
jurkat_data <- Read10X("../data/jurkat/filtered_matrices_mex/hg19/")
dim(jurkat_data)
```

```{r}
t_data <- Read10X("../data/293T/filtered_matrices_mex/hg19/")
dim(t_data)
```

```{r}
intersected_genes <- intersect(rownames(data3), intersect(rownames(jurkat_data), rownames(t_data)))
```

```{r}
data3_filt <- data3[match(intersected_genes, rownames(data3)), ]
jurkat_data_filt <- jurkat_data[match(intersected_genes, rownames(jurkat_data)),]
t_data_filt <- t_data[match(intersected_genes, rownames(t_data)),]
```

```{r}
dim(jurkat_data_filt)
dim(t_data_filt)
dim(data3_filt)
```

```{r}
pooled_data <- rbind(t(jurkat_data_filt), t(t_data_filt), t(data3_filt))
```

## Classification results (classtpx + svm)

### Full Gene set classtpx study

```{r}
class_labs <- c(rep("jurkat", dim(jurkat_data_filt)[2]), rep("293T", dim(t_data_filt)[2]))
class_labs_2 <- factor(as.vector(mapvalues(class_labs, from = unique(class_labs), to = 1:length(unique(class_labs)))))
known_indices <- 1:(dim(jurkat_data_filt)[2]+dim(t_data_filt)[2])
```

```{r echo=FALSE, eval=FALSE}
topic_clus <- class_topics(pooled_data, K=2, class_labs = class_labs_2, known_samples =known_indices, method = "theta.fix", shrink = FALSE, tol = 0.0001, ord=FALSE)
save(topic_clus, file = "../output/classtpx_jurkat_293T_99_1.rda")
```

```{r}
topic_clus <- get(load("../output/classtpx_jurkat_293T_99_1.rda"))
```


```{r}
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x) return(which.max(x))))
#labels2_class <- unique(class_labs)[labels2]

data_ggplot <- data.frame(labels2 = labels2[-known_indices],
                          tSNE_1 = seuratObj_TFH_global@tsne.rot[, 1],
                          tSNE_2 = seuratObj_TFH_global@tsne.rot[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels2), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```

We now compare this with the SVM based classification results.

### Reduced Gene set SVM study

```{r}
genes1 <- seuratObj_TFH_global@var.genes
```


```{r}
svm_data <- pooled_data[, match(genes1, colnames(pooled_data))]
```

```{r}
train_data <- as.matrix(svm_data[known_indices,])
test_data <- as.matrix(svm_data[-known_indices,])
y <- class_labs_2
dat <- cbind.data.frame(y, train_data);
```

```{r}
svm.control.default <- list(scale = TRUE, type = NULL, kernel ="radial",
                              degree = 3,
                              coef0 = 0, cost = 1, nu = 0.5,
                              class.weights = NULL, cachesize = 40, tolerance = 0.001, 
                              epsilon = 0.1,
                              shrinking = TRUE, cross = 0, fitted = TRUE)
svm.control <- list()
svm.control <- modifyList(svm.control.default, svm.control)


model_SVM <- do.call(e1071::svm, append(list(formula = y ~ .,
                                                   data=dat,
                                                   probability=TRUE), svm.control))
prob  = predict(model_SVM, test_data, probability=TRUE)
table(prob)
```

```{r}
prob_mat <- as.matrix(attr(prob, "probabilities"))
labels3 <- as.factor(apply(prob_mat, 1, function(x) return(which.max(x))))
#labels2_class <- unique(class_labs)[labels2]

data_ggplot <- data.frame(labels3 = labels3,
                          tSNE_1 = seuratObj_TFH_global@tsne.rot[, 1],
                          tSNE_2 = seuratObj_TFH_global@tsne.rot[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels3), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```
```{r}
prob_mat <- as.matrix(attr(prob, "probabilities"))
#labels3 <- as.factor(apply(prob_mat, 1, function(x) return(which.max(x))))
#labels2_class <- unique(class_labs)[labels2]
labels3 <- as.factor(apply(prob_mat, 1, function(x)
  {
  if(max(x) > 0.7){
    return(which.max(x))
    }else{
      return(dim(prob_mat)[2]+1)
      }}))


data_ggplot <- data.frame(labels3 = labels3,
                          tSNE_1 = seuratObj_TFH_global@tsne.rot[, 1],
                          tSNE_2 = seuratObj_TFH_global@tsne.rot[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels3), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```

### Reduced Gene set classtpx study

```{r echo=FALSE, eval=TRUE}
topic_clus <- class_topics(svm_data, K=2, class_labs = class_labs_2, known_samples =known_indices, method = "theta.fix", shrink = FALSE, tol = 0.0001, ord=FALSE)
```


```{r}
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x) return(which.max(x))))
#labels2_class <- unique(class_labs)[labels2]

data_ggplot <- data.frame(labels2 = labels2[-known_indices],
                          tSNE_1 = seuratObj_TFH_global@tsne.rot[, 1],
                          tSNE_2 = seuratObj_TFH_global@tsne.rot[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels2), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```



```{r}
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x)
  {
  if(max(x) > 0.7){
    return(which.max(x))
    }else{
      return(dim(topic_clus$omega)[2]+1)
      }}))
#labels2_class <- unique(class_labs)[labels2]

data_ggplot <- data.frame(labels2 = labels2[-known_indices],
                          tSNE_1 = seuratObj_TFH_global@tsne.rot[, 1],
                          tSNE_2 = seuratObj_TFH_global@tsne.rot[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels2), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```


## Clustering results 

```{r}
topic_clus_list <- get(load("../output/maptpx_jurkat_293T_99_1.rda"))
```

```{r}
PlotCountClust <- function(topic_clus, fac){
  omega <- topic_clus$omega
  theta <- topic_clus$theta
  
  annotation <- data.frame(
    sample_id = paste0("X", 1:length(fac)),
    tissue_label = factor(fac,
                          levels = rev(unique(fac) ) ) );

  rownames(omega) <- annotation$sample_id;
  
  StructureGGplot(omega = omega,
                  annotation = annotation,
                  palette = RColorBrewer::brewer.pal(8, "Accent"),
                  yaxis_label = "Types",
                  order_sample = TRUE,
                  axis_tick = list(axis_ticks_length = .1,
                                   axis_ticks_lwd_y = .1,
                                   axis_ticks_lwd_x = .1,
                                   axis_label_size = 7,
                                   axis_label_face = "bold"))
}
```

### Structure Plot representation

```{r}
PlotCountClust(topic_clus_list[[2]], fac)
PlotCountClust(topic_clus_list[[3]], fac)
PlotCountClust(topic_clus_list[[4]], fac)
PlotCountClust(topic_clus_list[[5]], fac)
```

### t-SNE projection + CountClust coloring

```{r fig.height = 6, echo=FALSE, eval=TRUE}
labels2 <- as.factor(apply(topic_clus_list[[2]]$omega, 1, function(x) return(which.max(x))))
labels3 <- as.factor(apply(topic_clus_list[[3]]$omega, 1, function(x) return(which.max(x))))
labels4 <- as.factor(apply(topic_clus_list[[4]]$omega, 1, function(x) return(which.max(x))))
labels5 <- as.factor(apply(topic_clus_list[[5]]$omega, 1, function(x) return(which.max(x))))

data_ggplot <- data.frame(labels2 = labels2,
                          labels3 = labels3,
                          labels4 = labels4,
                          labels5 = labels5,
                          tSNE_1 = seuratObj_TFH_global@tsne.rot[, 1],
                          tSNE_2 = seuratObj_TFH_global@tsne.rot[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels2), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels3), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')

plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels4), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')

plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels5), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')


plot_grid(plot1, plot2, plot3, plot4, ncol = 2, align = 'v')
```
