---
title: "Prepare MASH output"
author: "Kushal K Dey"
date: "8/31/2017"
output: html_document
---

We are looking to find a suitable way to obtain thresholding on the genes used for the clastpx model. It seems that we have sorted cells already available, one way of getting hold of such
genes would be to use MASH (Urbut, Wang, Stephens 2017). We first prepare the input for applying MASH.

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(plyr)
library(classtpx)
library(CountClust)
library(maptpx)
library(ggplot2)
library(MAST)
library(GSEABase)
library(Seurat)
```


```{r}
seuratObj_TFH_global <- get(load("../output/seurat_pooled_sorted_unsorted_PBMC.rda"))
```

```{r}
data <- seuratObj_TFH_global@raw.data[,1:4500]
counts_sorted <- t(data)
```

```{r}
fac <- sapply(colnames(data), function(x) return(paste0(head(strsplit(x, "[_]")[[1]], -1), collapse="_")))
```

We perform log-2 CPM transform 

```{r}
voom_data <- t(limma::voom(data)$E)
```

```{r echo=FALSE, eval=FALSE}
betahat <- matrix(0, dim(voom_data)[2], length(unique(fac))-1)
sebetahat <- matrix(0, dim(voom_data)[2], length(unique(fac))-1)
```

```{r echo=FALSE, eval=FALSE}
for(l in 1:dim(voom_data)[2]){
  ss <- lm(voom_data[,l] ~ factor(fac))
  summ_ss <- summary(ss)
  betahat[l,] <-  summ_ss$coefficients[-1,1] - median(summ_ss$coefficients[-1,1])
  sebetahat[l,] <- summ_ss$coefficients[-1,2]
  if((l %% 1000) == 0){
    cat("WE are at iteration :", l, "\n")
  }
}

```


```{r echo=FALSE, eval=FALSE}
for(l in 1:dim(voom_data)[2]){
  tmp1 <- tapply(voom_data[,l], factor(fac), mean)
  tmp2 <- tapply(voom_data[,l], factor(fac), sd)
  tmp1 <- tmp1 - median(tmp1)
  betahat[l,] <-  tmp1
  sebetahat[l,] <- tmp2
  if((l %% 1000) == 0){
    cat("WE are at iteration :", l, "\n")
  }
}

```

```{r echo=FALSE, eval=FALSE}
ll <- list("betahat" = betahat, "sebetahat" = sebetahat)
save(ll, file = "../output/mash_input_immune.rda")
```

The mash output is loaded 

```{r}
mash_out <- get(load("../output/mash_immune_canonical.rda"))
```


```{r}
library(mashr)
barplot(get_estimated_pi(mash_out), las = 2, cex.names = 0.3)
```

We look at the LFDR (Local False Discovery Rate) for a particular gene of interest - NKG7.

```{r}
idx <- which(rownames(data) == "GNLY")
mash_out$result$lfdr[idx,]
```

Note that the LFDR is very small for the 7th class which indeed corresponds to the NK cells.

```{r}
levels(factor(fac))
```


```{r}

gene_list <-  vector(mode="list", length=length(levels(factor(fac))))

for(l in 1:length(gene_list)){
  tmp <- apply(mash_out$result$lfdr, 1, function(x) {
      if((x[l]) < 0.1 && min(x[-l])> 0.3){
        return(1)
      }else{
        return(0)
      }
})
  gene_list[[l]] <- which(tmp == 1)
}

```

```{r}
unlist(gene_list)
```

```{r}
rownames(data)[unlist(gene_list)]
```

The gene names list is saved to be used for thresholding.

```{r}
names(gene_list) <-  levels(factor(fac))
save(gene_list, file = "../output/list_of_genes_mash_sorted_immune.rda")
```

```{r}
num_genes <- unlist(lapply(gene_list, function(x) return(length(x))))
```

```{r}
idx2 <- which(num_genes > 0)
```


The genes in these two sets are 

```{r}
rownames(data)[gene_list[[idx2[1]]]]
```

```{r}
rownames(data)[gene_list[[idx2[2]]]]
```


```{r}
seuratObj_TFH_global <- get(load("../output/seurat_pooled_sorted_unsorted_PBMC.rda"))
```

We look at the t-SNE expression patterns of these genes 

## t-SNE expression + MASH derived genes 

```{r echo=FALSE, eval=TRUE}
cex.size = 2
genes <- rownames(data)[gene_list[[idx2[1]]]]
genes1 <- mygene::queryMany(genes, scopes = "symbol", fields="symbol", species="human")$symbol


data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ]
                          # Third = seuratObj_TFH_global@data[paste0(genes[3]), ] # LiveCells marker
                          # Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          # Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          # Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes1[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes1[2]))

# plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
#                                      panel.grid.major = element_blank(), 
#                                      panel.grid.minor = element_blank(), 
#                                      axis.text.y = element_blank(),
#                                      axis.text.x = element_blank(),
#                                      axis.ticks = element_blank(),
#                                      legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes1[3]))

# plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
#                                      panel.grid.major = element_blank(), 
#                                      panel.grid.minor = element_blank(), 
#                                      axis.text.y = element_blank(),
#                                      axis.text.x = element_blank(),
#                                      axis.ticks = element_blank(),
#                                      legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes1[4]))
# 
# plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
#                                      panel.grid.major = element_blank(), 
#                                      panel.grid.minor = element_blank(), 
#                                      axis.text.y = element_blank(),
#                                      axis.text.x = element_blank(),
#                                      axis.ticks = element_blank(),
#                                      legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes1[5]))
# 
# plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
#                                      panel.grid.major = element_blank(), 
#                                      panel.grid.minor = element_blank(), 
#                                      axis.text.y = element_blank(),
#                                      axis.text.x = element_blank(),
#                                      axis.ticks = element_blank(),
#                                      legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes1[6]))

plot_grid(plot1, plot2, ncol = 2, align = 'v')
```


```{r echo=FALSE, eval=TRUE, fig.height = 6}
cex.size = 2
genes <- rownames(data)[gene_list[[idx2[2]]]]
genes1 <- mygene::queryMany(genes, scopes = "symbol", fields="symbol", species="human")$symbol


data_ggplot <- data.frame(tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2],
                          First = seuratObj_TFH_global@data[paste0(genes[1]), ], 
                          Second = seuratObj_TFH_global@data[paste0(genes[2]), ]
                          # Third = seuratObj_TFH_global@data[paste0(genes[3]), ] # LiveCells marker
                          # Fourth = seuratObj_TFH_global@data[paste0(genes[4]), ], # LiveCells marker
                          # Fifth = seuratObj_TFH_global@data[paste0(genes[5]), ],
                          # Sixth = seuratObj_TFH_global@data[paste0(genes[6]), ],
                          # Seventh = seuratObj_TFH_global@data[paste0(genes[7]), ]
                          ) # effector t cell

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = First), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[1]), ], 0.2),  name = paste0(genes1[1]))

plot2 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Second), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[2]), ], 0.2),  name = paste0(genes1[2]))

# plot3 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
#                                      panel.grid.major = element_blank(), 
#                                      panel.grid.minor = element_blank(), 
#                                      axis.text.y = element_blank(),
#                                      axis.text.x = element_blank(),
#                                      axis.ticks = element_blank(),
#                                      legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Third), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[3]), ], 0.2),  name = paste0(genes1[3]))

# plot4 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
#                                      panel.grid.major = element_blank(), 
#                                      panel.grid.minor = element_blank(), 
#                                      axis.text.y = element_blank(),
#                                      axis.text.x = element_blank(),
#                                      axis.ticks = element_blank(),
#                                      legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fourth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[4]), ], 0.2),  name = paste0(genes1[4]))
# 
# plot5 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
#                                      panel.grid.major = element_blank(), 
#                                      panel.grid.minor = element_blank(), 
#                                      axis.text.y = element_blank(),
#                                      axis.text.x = element_blank(),
#                                      axis.ticks = element_blank(),
#                                      legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Fifth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[5]), ], 0.2),  name = paste0(genes1[5]))
# 
# plot6 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
#                                      panel.grid.major = element_blank(), 
#                                      panel.grid.minor = element_blank(), 
#                                      axis.text.y = element_blank(),
#                                      axis.text.x = element_blank(),
#                                      axis.ticks = element_blank(),
#                                      legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[6]), ], 0.2),  name = paste0(genes1[6]))
# 
# plot7 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
#                                      panel.grid.major = element_blank(), 
#                                      panel.grid.minor = element_blank(), 
#                                      axis.text.y = element_blank(),
#                                      axis.text.x = element_blank(),
#                                      axis.ticks = element_blank(),
#                                      legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = Sixth), size = cex.size) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_colour_gradient2(low = 'royalblue', high = 'red', mid = 'grey80', midpoint = quantile(seuratObj_TFH_global@data[paste0(genes[7]), ], 0.2),  name = paste0(genes1[7]))

plot_grid(plot1, plot2, ncol = 2, align = 'v')
```


```{r}
genes_counter <- apply(mash_out$result$lfdr, 1, function(x){
  if(min(x) < 0.7){return(1)}else{return(0)}
})
```

```{r}
idx_counter <- which(genes_counter == 1)
imp_genes <- rownames(data)[idx_counter]
```

```{r}
imp_genes
```

So these seem to be the only genes with at least one lfdr value less than 0.7.


