---
title: "Cluster analysis of the PBMC  Oct, 2016"
author: "Kushal K Dey"
date: "8/4/2017"
output: html_document
---

We look at the cluster patterns of the PBMC cluster data for Oct 2016.

```{r}
library(CountClust)
library(maptpx)
library(ggplot2)
library(MAST)
library(GSEABase)
```

```{r}
counts6 <- get(load("../output/GS_PBMC_2_2015_GRN0304.rda"))
counts6 <- as.matrix(counts6)
```

## Cluster analysis

```{r}
topic_clus <- get(load("../output/maptpx_GS_PBMC_2_2015_GRN0304.rda"))
```

```{r}
fac <- rep("PBMC-2-2015", dim(counts6)[1])
```

```{r}
PlotCountClust <- function(topic_clus, fac){
  omega <- topic_clus$omega
  theta <- topic_clus$theta
  
  annotation <- data.frame(
    sample_id = paste0("X", 1:length(fac)),
    tissue_label = factor(fac,
                          levels = rev(unique(fac) ) ) );

  rownames(omega) <- annotation$sample_id;
  
  StructureGGplot(omega = omega,
                  annotation = annotation,
                  palette = RColorBrewer::brewer.pal(8, "Accent"),
                  yaxis_label = "Types",
                  order_sample = TRUE,
                  axis_tick = list(axis_ticks_length = .1,
                                   axis_ticks_lwd_y = .1,
                                   axis_ticks_lwd_x = .1,
                                   axis_label_size = 7,
                                   axis_label_face = "bold"))
}
```

```{r}
PlotCountClust(topic_clus[[2]], fac)
PlotCountClust(topic_clus[[3]], fac)
PlotCountClust(topic_clus[[4]], fac)
PlotCountClust(topic_clus[[5]], fac)
PlotCountClust(topic_clus[[6]], fac)
```

What do these clusters represent?

We look at the top genes for the cluster for $K=3$. Also we perform a GSEA of the top driving genes for each cluster.

```{r}
indices <- ExtractTopFeatures(topic_clus[[3]]$theta, top_features = 100, method = "poisson", options = "max")
imp_genes <- apply(indices, 1, function(x) return(colnames(counts6)[x]))
```

### cluster 1 K = 3

```{r}
out <- mygene::queryMany(imp_genes[1:50,1],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
```

### cluster 2 K = 3

```{r}
out <- mygene::queryMany(imp_genes[1:50,2],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
```

### cluster 3 K = 3

```{r}
out <- mygene::queryMany(imp_genes[1:50,3],  scopes="symbol", fields=c("symbol", "name", "summary"), species="human");
cbind.data.frame(out$symbol[!is.na(out$summary)], out$name[!is.na(out$summary)])
```


## GSEA 

We perform gene set enrichment analysis on the theta matrices, reprsenting the three clusters, obtained from fitting CountClust on the Live + LN cells.

```{r}
theta <- topic_clus[[3]]$theta
theta2 <- t(apply(theta, 1, function(x) return((x - mean(x))/sd(x))))
```

We extract gene names in pathways from the MAST package 

```{r}
module <- "BTM"
min_gene_in_module <- 5
packageExt <- system.file("extdata", package='MAST')
module_file <- list.files(packageExt, pattern = module, full.names = TRUE)
gene_set <- getGmt(module_file)
gene_ids <- geneIds(gene_set)
```

### First cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,1])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),]
```

### Second cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,2])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),]
```

### Third cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,3])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),]
```

