---
title: "Separate CountClust on PBMC and LN cells for TFH cells (TFH146)"
author: "Kushal K Dey"
date: "7/27/2017"
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(Seurat)
library(plyr)
library(dplyr)
library(Matrix)
library(cowplot)
library(stringr)
library(MAST)
library(doMC)
library(pheatmap)
library(grid)
library(stringr)
library(maptpx)
library(CountClust)
library(ggplot2)
library(GGally)
library(GSEABase)
library(limma)
library(reshape2)
library(data.table)
library(knitr)
library(TxDb.Hsapiens.UCSC.hg19.knownGene)
library(stringr)
library(NMF)
library(rsvd)
library(RColorBrewer)
library(MAST)
```

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
TFH_LN_UMI <- read.table('../data/TFH146/TFH Sorted/LN/reads.TFH146_TFH_LN_S1_R1_001.fastq_bq10_star_corrected.umi.dge.txt.gz', header = TRUE, row.names = 1)
TFH_LN_reads <- read.table('../data/TFH146/TFH Sorted/LN/reads.TFH146_TFH_LN_S1_R1_001.fastq_bq10_star_corrected.reads.dge.txt.gz', header = TRUE, row.names = 1)
TFH_LN_UMI_summary <- read.table('../data/TFH146/TFH Sorted/LN/reads.TFH146_TFH_LN_S1_R1_001.fastq_bq10_star_corrected.umi.dge.summary.txt', header = TRUE, row.names = 1)
TFH_LN_reads_summary <- read.table('../data/TFH146/TFH Sorted/LN/reads.TFH146_TFH_LN_S1_R1_001.fastq_bq10_star_corrected.reads.dge.summary.txt', header = TRUE, row.names = 1)
#- First filtering - remove cells with less than 10 genes
TFH_LN_UMI <- TFH_LN_UMI[, rownames(TFH_LN_reads_summary)[which(TFH_LN_reads_summary$NUM_GENES > 10)]]
TFH_LN_reads <- TFH_LN_reads[, rownames(TFH_LN_reads_summary)[which(TFH_LN_reads_summary$NUM_GENES > 10)]]
TFH_LN_UMI_summary <- TFH_LN_UMI_summary[colnames(TFH_LN_UMI), ]
TFH_LN_reads_summary <- TFH_LN_reads_summary[colnames(TFH_LN_reads), ]

##- PBMC
TFH_PBMC_UMI <- read.table('../data/TFH146/TFH Sorted/PBMC/reads.TFH146_TFH_PBMC_S2_R1_001.fastq_bq10_star_corrected.umi.dge.txt.gz', header = TRUE, row.names = 1)
TFH_PBMC_reads <- read.table('../data/TFH146/TFH Sorted/PBMC/reads.TFH146_TFH_PBMC_S2_R1_001.fastq_bq10_star_corrected.reads.dge.txt.gz', header = TRUE, row.names = 1)
TFH_PBMC_UMI_summary <- read.table('../data/TFH146/TFH Sorted/PBMC/reads.TFH146_TFH_PBMC_S2_R1_001.fastq_bq10_star_corrected.umi.dge.summary.txt', header = TRUE, row.names = 1)
TFH_PBMC_reads_summary <- read.table('../data/TFH146/TFH Sorted/PBMC/reads.TFH146_TFH_PBMC_S2_R1_001.fastq_bq10_star_corrected.reads.dge.summary.txt', header = TRUE, row.names = 1)
#- First filtering - remove cells with less than 10 genes
TFH_PBMC_UMI <- TFH_PBMC_UMI[, rownames(TFH_PBMC_reads_summary)[which(TFH_PBMC_reads_summary$NUM_GENES > 10)]]
TFH_PBMC_reads <- TFH_PBMC_reads[, rownames(TFH_PBMC_reads_summary)[which(TFH_PBMC_reads_summary$NUM_GENES > 10)]]
TFH_PBMC_UMI_summary <- TFH_PBMC_UMI_summary[colnames(TFH_PBMC_UMI), ]
TFH_PBMC_reads_summary <- TFH_PBMC_reads_summary[colnames(TFH_PBMC_reads), ]
```

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
identical(colnames(TFH_LN_UMI), rownames(TFH_LN_UMI_summary)) # TRUE
TFH_LN_UMI_filtered <- TFH_LN_UMI[, which(TFH_LN_UMI_summary$NUM_GENES >= 400 & TFH_LN_UMI_summary$NUM_TRANSCRIPTS >= 750)] 
TFH_LN_UMI_filtered <- TFH_LN_UMI_filtered[which(apply(TFH_LN_UMI_filtered, 1, sum) != 0), ] # 
identical(colnames(TFH_PBMC_UMI), rownames(TFH_PBMC_UMI_summary)) # TRUE
TFH_PBMC_UMI_filtered <- TFH_PBMC_UMI[, which(TFH_PBMC_UMI_summary$NUM_GENES >= 400 & TFH_PBMC_UMI_summary$NUM_TRANSCRIPTS >= 750)] 
TFH_PBMC_UMI_filtered <- TFH_PBMC_UMI_filtered[which(apply(TFH_PBMC_UMI_filtered, 1, sum) != 0), ] 
TFH_UMI <- rbind.fill(as.data.frame(t(TFH_LN_UMI_filtered)), as.data.frame(t(TFH_PBMC_UMI_filtered)))
rownames(TFH_UMI) <- c(paste(colnames(TFH_LN_UMI_filtered), 'LN', sep = '_'), paste(colnames(TFH_PBMC_UMI_filtered), 'PBMC', sep = '_'))
dim(TFH_UMI) 
length(unique(c(rownames(TFH_LN_UMI_filtered), rownames(TFH_PBMC_UMI_filtered)))) 
TFH_UMI[is.na(TFH_UMI)] <- 0 
TFH_UMI <- as.data.frame(t(TFH_UMI))
```

```{r echo=FALSE, eval=TRUE}
TFH_fac <- c(rep("TFH_LN", dim(TFH_LN_UMI_filtered)[2]),
             rep("TFH_PBMC", dim(TFH_PBMC_UMI_filtered)[2]))
length(TFH_fac)
```

```{r echo=FALSE, eval=TRUE}
counts <- t(TFH_UMI)
idx <- which(!is.na(match(substring(colnames(counts), 1, 2), c("RP", "MT", "RN"))))
counts2 <- counts[, -idx]
```

```{r}
counts2LN <- counts2[which(TFH_fac == "TFH_LN"),]
counts2PBMC <- counts2[which(TFH_fac == "TFH_PBMC"),]
```


# CountClust on LN cells (TFH)

```{r}
idx3 <- match(c("MALAT1", "B2M", "TMSB4X", "TMSB10"), colnames(counts2LN))
counts3LN <- counts2LN[,-idx3]
counts3PBMC <- counts2PBMC[,-idx3]
```


```{r echo=FALSE, eval=FALSE}
topic_clus_list <- list()
for(k in 2:4){
  topic_clus_list[[k]] <- maptpx::topics(counts3LN, K=k, tol = 10)
}
save(topic_clus_list, file = "../output/TFH146/LN_TFH/model2.rda")
```

```{r echo=FALSE, eval=TRUE}
PlotCountClust <- function(topic_clus, fac){
  omega <- topic_clus$omega
  theta <- topic_clus$theta
  
  annotation <- data.frame(
    sample_id = paste0("X", 1:length(fac)),
    tissue_label = factor(fac,
                          levels = rev(unique(fac) ) ) );

  rownames(omega) <- annotation$sample_id;
  
  StructureGGplot(omega = omega,
                  annotation = annotation,
                  palette = RColorBrewer::brewer.pal(8, "Accent"),
                  yaxis_label = "Types",
                  order_sample = TRUE,
                  axis_tick = list(axis_ticks_length = .1,
                                   axis_ticks_lwd_y = .1,
                                   axis_ticks_lwd_x = .1,
                                   axis_label_size = 7,
                                   axis_label_face = "bold"))
}
```


```{r}
topic_clus_list <- get(load("../output/TFH146/LN_TFH/model2.rda"))
PlotCountClust(topic_clus_list[[2]], factor(TFH_fac[which(TFH_fac == "TFH_LN")]))
PlotCountClust(topic_clus_list[[3]], factor(TFH_fac[which(TFH_fac == "TFH_LN")]))
PlotCountClust(topic_clus_list[[4]], TFH_fac[which(TFH_fac == "TFH_LN")])
```

With and without MALAT1 and B2M, the big expressed genes, the results look pretty similar. We extract the top driving genes for the three three clusters case.

## Annotating Top genes (K=3)

```{r}
indices <- ExtractTopFeatures(topic_clus_list[[3]]$theta, top_features = 100, method = "poisson", options = "max")
imp_genes <- apply(indices, 1, function(x) return(colnames(counts2)[x]))
```

### cluster 1 K = 3

```{r}
out <- mygene::queryMany(imp_genes[1:50,1],  scopes="symbol", fields=c("name", "summary"), species="human");
cbind.data.frame(out$name)
```

### cluster 2 K = 3

```{r}
out <- mygene::queryMany(imp_genes[1:50,2],  scopes="symbol", fields=c("name", "summary"), species="human");
cbind.data.frame(out$name)
```

### cluster 3 K = 3

```{r}
out <- mygene::queryMany(imp_genes[1:50,3],  scopes="symbol", fields=c("name", "summary"), species="human");
cbind.data.frame(out$name)
```

## GSEA 

We perform gene set enrichment analysis on the theta matrices, reprsenting the three clusters, obtained from fitting CountClust on the TFH + LN cells.

```{r}
theta <- topic_clus_list[[3]]$theta
theta2 <- t(apply(theta, 1, function(x) return((x - mean(x))/sd(x))))
```

We extract gene names in pathways from the MAST package 

```{r}
module <- "BTM"
min_gene_in_module <- 5
packageExt <- system.file("extdata", package='MAST')
module_file <- list.files(packageExt, pattern = module, full.names = TRUE)
gene_set <- getGmt(module_file)
gene_ids <- geneIds(gene_set)
```

### First cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,1])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),]
```

### Second cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,2])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),]
```

### Third cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,3])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),]
```


# CountClust on PBMC cells (TFH)

```{r echo=FALSE, eval=FALSE}
topic_clus_list <- list()
for(k in 2:4){
  topic_clus_list[[k]] <- maptpx::topics(counts3PBMC, K=k, tol = 10)
}
save(topic_clus_list, file = "../output/TFH146/PBMC_TFH/model2.rda")
```


```{r}
topic_clus_list <- get(load("../output/TFH146/PBMC_TFH/model2.rda"))
PlotCountClust(topic_clus_list[[2]], factor(TFH_fac[which(TFH_fac == "TFH_PBMC")]))
PlotCountClust(topic_clus_list[[3]], factor(TFH_fac[which(TFH_fac == "TFH_PBMC")]))
PlotCountClust(topic_clus_list[[4]], TFH_fac[which(TFH_fac == "TFH_PBMC")])
```


## Annotating Top genes (K=3)

```{r}
indices <- ExtractTopFeatures(topic_clus_list[[3]]$theta, top_features = 100, method = "poisson", options = "max")
imp_genes <- apply(indices, 1, function(x) return(colnames(counts2)[x]))
```

### cluster 1 K = 3

```{r}
out <- mygene::queryMany(imp_genes[1:50,1],  scopes="symbol", fields=c("name", "summary"), species="human");
cbind.data.frame(out$name)
```

### cluster 2 K = 3

```{r}
out <- mygene::queryMany(imp_genes[1:50,2],  scopes="symbol", fields=c("name", "summary"), species="human");
cbind.data.frame(out$name)
```

### cluster 3 K = 3

```{r}
out <- mygene::queryMany(imp_genes[1:50,3],  scopes="symbol", fields=c("name", "summary"), species="human");
cbind.data.frame(out$name)
```

## GSEA 

We perform gene set enrichment analysis on the theta matrices, reprsenting the three clusters, obtained from fitting CountClust on the TFH + LN cells.

```{r}
theta <- topic_clus_list[[3]]$theta
theta2 <- t(apply(theta, 1, function(x) return((x - mean(x))/sd(x))))
```

We extract gene names in pathways from the MAST package 

```{r}
module <- "BTM"
min_gene_in_module <- 5
packageExt <- system.file("extdata", package='MAST')
module_file <- list.files(packageExt, pattern = module, full.names = TRUE)
gene_set <- getGmt(module_file)
gene_ids <- geneIds(gene_set)
```

### First cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,1])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),]
```

### Second cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,2])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),]
```

### Third cluster pre-ranked GSEA

```{r echo=FALSE, eval=TRUE}
vec <- as.vector(theta2[,3])
names(vec) <- rownames(theta)
vec2 <- (vec - mean(vec))/sd(vec)
out <- fgsea::fgsea(gene_ids, vec2, minSize=1,
                  maxSize=500,
                  nperm=10000)
mm <- cbind.data.frame(out$padj, out$size)
mm$topgenes <- out$leadingEdge
rownames(mm) <- names(gene_ids)[as.numeric(rownames(mm))]
mm[order(mm$`out$padj`, decreasing = FALSE),]
```




