---
title: "Support Vector Machines (SVM) and classtpx on PBMC data"
author: "Kushal K Dey"
date: "8/28/2017"
output: html_document
---

We look at the t-SNE visualizations of the classtpx and the SVM model fits on the 
PBMC data.

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(CountClust)
library(maptpx)
library(ggplot2)
library(GSEABase)
library(Seurat)
library(classtpx)
library(e1071)
```

```{r echo=FALSE, eval=TRUE}
seuratObj_TFH_global <- get(load("../output/seurat_pooled_sorted_unsorted_PBMC.rda"))
```


```{r echo=FALSE, eval=TRUE}
data <- seuratObj_TFH_global@raw.data
counts <- t(data)
```

```{r echo=FALSE, eval=TRUE}
fac1 <- sapply(colnames(data)[1:4500], function(x) return(paste0(head(strsplit(x, "[_]")[[1]], -1), collapse="_")))
class_labs_train <- fac1
```


```{r echo=FALSE, eval=TRUE}
pca_data <- seuratObj_TFH_global@dr$pca@cell.embeddings
```

```{r echo=FALSE, eval=TRUE}
train_indices <- 1:4500
test_indices <- 4501:9500
trainX <- pca_data[train_indices,]
testX <- pca_data[test_indices,]
y = factor(class_labs_train)
dat <- cbind.data.frame(y, trainX);
```

## SVM application

```{r echo=TRUE, eval=TRUE}
svm.control.default <- list(scale = TRUE, type = NULL, kernel ="radial",
                              degree = 3,
                              coef0 = 0, cost = 1, nu = 0.5,
                              class.weights = NULL, cachesize = 40, tolerance = 0.001, 
                              epsilon = 0.1,
                              shrinking = TRUE, cross = 0, fitted = TRUE)
svm.control <- list()
svm.control <- modifyList(svm.control.default, svm.control)


model_SVM <- do.call(e1071::svm, append(list(formula = y ~ .,
                                                   data=dat,
                                                   probability=TRUE), svm.control))
prob  = predict(model_SVM, testX, probability=TRUE)
table(prob)
```

```{r echo=FALSE, eval=TRUE}
labels2 <- as.vector(prob)
labels2_class <- c(fac1, labels2)

data_ggplot <- data.frame(labels2_class = labels2_class,
                          tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels2_class), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```

We contrast this with the picture from classtpx model fit.

## classtpx fit

```{r echo=FALSE, eval=TRUE}
topic_clus <- get(load("../output/classtpx_pbmc_68K_no_thresh.rda"))
```

```{r echo=FALSE, eval=TRUE}
fac1 <- sapply(colnames(data)[1:4500], function(x) return(paste0(head(strsplit(x, "[_]")[[1]], -1), collapse="_")))
known_samples <- 1:4500
class_labs <- fac1
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x) return(which.max(x))))
labels2_class <- unique(class_labs)[labels2]

data_ggplot <- data.frame(labels2_class = labels2_class,
                          tSNE_1 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 1],
                          tSNE_2 = seuratObj_TFH_global@dr$tsne@cell.embeddings[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels2_class), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```

## tSNE comparative analysis : SVM vs classtpx

We present a comparative analysis of the class memberships from the SVM method and the classtpx method.

```{r}
probs_mat <- attr(prob, "probabilities")
dim(probs_mat)
colnames(probs_mat)
```

```{r}
mat1 <- matrix(0, nrow=4500, ncol=9)
colnames(mat1) <- colnames(probs_mat)
for(m in 1:4500){
  mat1[m, match(y[m], colnames(mat1))] <- 1
}
```

```{r}
pooled_mat <- rbind(mat1, probs_mat)
```

```{r echo=FALSE, eval=FALSE}
save(pooled_mat, file = "../output/svm_memberships.rda")
omega <- topic_clus$omega
save(omega, file = "../output/classtpx_memberships.rda")
```

```{r echo=FALSE, eval=TRUE}
tsne_svm_memberships <- get(load("../output/tsne_svm_memberships.rda"))
tsne_classtpx_memberships <- get(load("../output/tsne_classtpx_memberships.rda"))
dim(tsne_classtpx_memberships)
dim(tsne_svm_memberships)
```

### classtpx labels on classtpx tSNE

```{r echo=FALSE, eval=TRUE}
fac1 <- sapply(colnames(data)[1:4500], function(x) return(paste0(head(strsplit(x, "[_]")[[1]], -1), collapse="_")))
known_samples <- 1:4500
class_labs <- fac1
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x) return(which.max(x))))
labels2_class <- unique(class_labs)[labels2]

data_ggplot <- data.frame(labels2_class = labels2_class,
                          tSNE_1 = tsne_classtpx_memberships[, 1],
                          tSNE_2 = tsne_classtpx_memberships[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels2_class), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```

### SVM labels on classtpx tSNE

```{r echo=FALSE, eval=TRUE}
labels2_class <- as.factor(c(as.character(y), as.character(prob[1:5000])))
data_ggplot <- data.frame(labels2_class = labels2_class,
                          tSNE_1 = tsne_classtpx_memberships[, 1],
                          tSNE_2 = tsne_classtpx_memberships[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels2_class), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```

### classtpx labels on SVM tSNE

```{r echo=FALSE, eval=TRUE}
fac1 <- sapply(colnames(data)[1:4500], function(x) return(paste0(head(strsplit(x, "[_]")[[1]], -1), collapse="_")))
known_samples <- 1:4500
class_labs <- fac1
labels2 <- as.factor(apply(topic_clus$omega, 1, function(x) return(which.max(x))))
labels2_class <- unique(class_labs)[labels2]

data_ggplot <- data.frame(labels2_class = labels2_class,
                          tSNE_1 = tsne_svm_memberships[, 1],
                          tSNE_2 = tsne_svm_memberships[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels2_class), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```

### SVM labels on SVM tSNE

```{r echo=FALSE, eval=TRUE}
labels2_class <- as.factor(c(as.character(y), as.character(prob[1:5000])))
data_ggplot <- data.frame(labels2_class = labels2_class,
                          tSNE_1 = tsne_svm_memberships[, 1],
                          tSNE_2 = tsne_svm_memberships[, 2])

plot1 <- ggplot(data_ggplot) + theme(panel.background = element_rect(colour = "black", size = 1), 
                                     panel.grid.major = element_blank(), 
                                     panel.grid.minor = element_blank(), 
                                     axis.text.y = element_blank(),
                                     axis.text.x = element_blank(),
                                     axis.ticks = element_blank(),
                                     legend.text = element_text(size = 15)) + geom_point(aes(x = tSNE_1, y = tSNE_2, color = labels2_class), size = 0.5) + labs(x = 'tSNE 1', y = 'tSNE 2', title = '') + scale_color_discrete('')
plot1
```

